---
title: "CarexLinkageMap"
author: "amesclir"
date: "05/05/2015"
output: html_document
---

First, we load the package onemap and import the data set

```{r}

library (onemap)

f2.onemap <- read_mapmaker(file = "onemap.f2.txt")

```

Second, we assign markers to linkage groups

```{r}
twopts <- rf_2pts(f2.onemap, LOD=3, max.rf=0.5)
mark.all <- make_seq(twopts, "all")
LGs.f2.6.0.5 <- group(mark.all, LOD = 6, max.rf = 0.5)
LGs.f2.6.0.5 
```

Third, we get the genetic mapping of linkage groups

```{r}
set.map.fun(type="kosambi")

LG.f2.6.0.5.1 <- make_seq(LGs.f2.6.0.5, 1)
LG.f2.6.0.5.2 <- make_seq(LGs.f2.6.0.5, 2)
LG.f2.6.0.5.3 <- make_seq(LGs.f2.6.0.5, 3)
LG.f2.6.0.5.4 <- make_seq(LGs.f2.6.0.5, 4)
LG.f2.6.0.5.5 <- make_seq(LGs.f2.6.0.5, 5)
LG.f2.6.0.5.6 <- make_seq(LGs.f2.6.0.5, 6)
LG.f2.6.0.5.7 <- make_seq(LGs.f2.6.0.5, 7)
LG.f2.6.0.5.8 <- make_seq(LGs.f2.6.0.5, 8)
LG.f2.6.0.5.9 <- make_seq(LGs.f2.6.0.5, 9)
LG.f2.6.0.5.10 <- make_seq(LGs.f2.6.0.5, 10)
LG.f2.6.0.5.11 <- make_seq(LGs.f2.6.0.5, 11)
LG.f2.6.0.5.12 <- make_seq(LGs.f2.6.0.5, 12)
LG.f2.6.0.5.13 <- make_seq(LGs.f2.6.0.5, 13)
LG.f2.6.0.5.14 <- make_seq(LGs.f2.6.0.5, 14)
LG.f2.6.0.5.15 <- make_seq(LGs.f2.6.0.5, 15)
LG.f2.6.0.5.16 <- make_seq(LGs.f2.6.0.5, 16)
LG.f2.6.0.5.17 <- make_seq(LGs.f2.6.0.5, 17)
LG.f2.6.0.5.18 <- make_seq(LGs.f2.6.0.5, 18)
LG.f2.6.0.5.19 <- make_seq(LGs.f2.6.0.5, 19)
LG.f2.6.0.5.20 <- make_seq(LGs.f2.6.0.5, 20)
LG.f2.6.0.5.21 <- make_seq(LGs.f2.6.0.5, 21)
LG.f2.6.0.5.22 <- make_seq(LGs.f2.6.0.5, 22)
LG.f2.6.0.5.23 <- make_seq(LGs.f2.6.0.5, 23)
LG.f2.6.0.5.24 <- make_seq(LGs.f2.6.0.5, 24)
LG.f2.6.0.5.25 <- make_seq(LGs.f2.6.0.5, 25)
LG.f2.6.0.5.26 <- make_seq(LGs.f2.6.0.5, 26)
LG.f2.6.0.5.27 <- make_seq(LGs.f2.6.0.5, 27)
LG.f2.6.0.5.28 <- make_seq(LGs.f2.6.0.5, 28)
LG.f2.6.0.5.29 <- make_seq(LGs.f2.6.0.5, 29)
LG.f2.6.0.5.30 <- make_seq(LGs.f2.6.0.5, 30)
LG.f2.6.0.5.31 <- make_seq(LGs.f2.6.0.5, 31)
LG.f2.6.0.5.32 <- make_seq(LGs.f2.6.0.5, 32)




LG.f2.6.0.5.1.ord <- order_seq(LG.f2.6.0.5.1, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.2.ord <- order_seq(LG.f2.6.0.5.2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.3.ord <- order_seq(LG.f2.6.0.5.3, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.4.ord <- order_seq(LG.f2.6.0.5.4, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.5.ord <- order_seq(LG.f2.6.0.5.5, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.6.ord <- order_seq(LG.f2.6.0.5.6, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.7.ord <- order_seq(LG.f2.6.0.5.7, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.8.ord <- order_seq(LG.f2.6.0.5.8, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.9.ord <- order_seq(LG.f2.6.0.5.9, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.10.ord <- order_seq(LG.f2.6.0.5.10, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.11.ord <- order_seq(LG.f2.6.0.5.11, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.12.ord <- order_seq(LG.f2.6.0.5.12, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.13.ord <- order_seq(LG.f2.6.0.5.13, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.14.ord <- order_seq(LG.f2.6.0.5.14, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.15.ord <- order_seq(LG.f2.6.0.5.15, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.16.ord <- order_seq(LG.f2.6.0.5.16, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.17.ord <- order_seq(LG.f2.6.0.5.17, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.18.ord <- order_seq(LG.f2.6.0.5.18, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.19.ord <- order_seq(LG.f2.6.0.5.19, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.20.ord <- order_seq(LG.f2.6.0.5.20, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.21.ord <- order_seq(LG.f2.6.0.5.21, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.22.ord <- order_seq(LG.f2.6.0.5.22, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.23.ord <- order_seq(LG.f2.6.0.5.23, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.24.ord <- order_seq(LG.f2.6.0.5.24, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.25.ord <- order_seq(LG.f2.6.0.5.25, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.26.ord <- order_seq(LG.f2.6.0.5.26, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.27.ord <- order_seq(LG.f2.6.0.5.27, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.28.ord <- order_seq(LG.f2.6.0.5.28, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.29.ord <- order_seq(LG.f2.6.0.5.29, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.30.ord <- order_seq(LG.f2.6.0.5.30, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.31.ord <- order_seq(LG.f2.6.0.5.31, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.32.ord <- order_seq(LG.f2.6.0.5.32, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)


```

Now, we order the markers, all of them and only the safe ones

```{r}
LG.f2.6.0.5.1.ord.safe <- make_seq(LG.f2.6.0.5.1.ord,"safe")
LG.f2.6.0.5.2.ord.safe <- make_seq(LG.f2.6.0.5.2.ord,"safe")
LG.f2.6.0.5.3.ord.safe <- make_seq(LG.f2.6.0.5.3.ord,"safe")
LG.f2.6.0.5.4.ord.safe <- make_seq(LG.f2.6.0.5.4.ord,"safe")
LG.f2.6.0.5.5.ord.safe <- make_seq(LG.f2.6.0.5.5.ord,"safe")
LG.f2.6.0.5.6.ord.safe <- make_seq(LG.f2.6.0.5.6.ord,"safe")
LG.f2.6.0.5.7.ord.safe <- make_seq(LG.f2.6.0.5.7.ord,"safe")
LG.f2.6.0.5.8.ord.safe <- make_seq(LG.f2.6.0.5.8.ord,"safe")
LG.f2.6.0.5.9.ord.safe <- make_seq(LG.f2.6.0.5.9.ord,"safe")
LG.f2.6.0.5.10.ord.safe <- make_seq(LG.f2.6.0.5.10.ord,"safe")
LG.f2.6.0.5.11.ord.safe <- make_seq(LG.f2.6.0.5.11.ord,"safe")
LG.f2.6.0.5.12.ord.safe <- make_seq(LG.f2.6.0.5.12.ord,"safe")
LG.f2.6.0.5.13.ord.safe <- make_seq(LG.f2.6.0.5.13.ord,"safe")
LG.f2.6.0.5.14.ord.safe <- make_seq(LG.f2.6.0.5.14.ord,"safe")
LG.f2.6.0.5.15.ord.safe <- make_seq(LG.f2.6.0.5.15.ord,"safe")
LG.f2.6.0.5.16.ord.safe <- make_seq(LG.f2.6.0.5.16.ord,"safe")
LG.f2.6.0.5.17.ord.safe <- make_seq(LG.f2.6.0.5.17.ord,"safe")
LG.f2.6.0.5.18.ord.safe <- make_seq(LG.f2.6.0.5.18.ord,"safe")
LG.f2.6.0.5.19.ord.safe <- make_seq(LG.f2.6.0.5.19.ord,"safe")
LG.f2.6.0.5.20.ord.safe <- make_seq(LG.f2.6.0.5.20.ord,"safe")
LG.f2.6.0.5.21.ord.safe <- make_seq(LG.f2.6.0.5.21.ord,"safe")
LG.f2.6.0.5.22.ord.safe <- make_seq(LG.f2.6.0.5.22.ord,"safe")
LG.f2.6.0.5.23.ord.safe <- make_seq(LG.f2.6.0.5.23.ord,"safe")
LG.f2.6.0.5.24.ord.safe <- make_seq(LG.f2.6.0.5.24.ord,"safe")
LG.f2.6.0.5.25.ord.safe <- make_seq(LG.f2.6.0.5.25.ord,"safe")
LG.f2.6.0.5.26.ord.safe <- make_seq(LG.f2.6.0.5.26.ord,"safe")
LG.f2.6.0.5.27.ord.safe <- make_seq(LG.f2.6.0.5.27.ord,"safe")
LG.f2.6.0.5.28.ord.safe <- make_seq(LG.f2.6.0.5.28.ord,"safe")
LG.f2.6.0.5.29.ord.safe <- make_seq(LG.f2.6.0.5.29.ord,"safe")
LG.f2.6.0.5.30.ord.safe <- make_seq(LG.f2.6.0.5.30.ord,"safe")
LG.f2.6.0.5.31.ord.safe <- make_seq(LG.f2.6.0.5.31.ord,"safe")
LG.f2.6.0.5.32.ord.safe <- make_seq(LG.f2.6.0.5.32.ord,"safe")

LG.f2.6.0.5.1.ord.all <- make_seq(LG.f2.6.0.5.1.ord,"force")
LG.f2.6.0.5.2.ord.all <- make_seq(LG.f2.6.0.5.2.ord,"force")
LG.f2.6.0.5.3.ord.all <- make_seq(LG.f2.6.0.5.3.ord,"force")
LG.f2.6.0.5.4.ord.all <- make_seq(LG.f2.6.0.5.4.ord,"force")
LG.f2.6.0.5.5.ord.all <- make_seq(LG.f2.6.0.5.5.ord,"force")
LG.f2.6.0.5.6.ord.all <- make_seq(LG.f2.6.0.5.6.ord,"force")
LG.f2.6.0.5.7.ord.all <- make_seq(LG.f2.6.0.5.7.ord,"force")
LG.f2.6.0.5.8.ord.all <- make_seq(LG.f2.6.0.5.8.ord,"force")
LG.f2.6.0.5.9.ord.all <- make_seq(LG.f2.6.0.5.9.ord,"force")
LG.f2.6.0.5.10.ord.all <- make_seq(LG.f2.6.0.5.10.ord,"force")
LG.f2.6.0.5.11.ord.all <- make_seq(LG.f2.6.0.5.11.ord,"force")
LG.f2.6.0.5.12.ord.all <- make_seq(LG.f2.6.0.5.12.ord,"force")
LG.f2.6.0.5.13.ord.all <- make_seq(LG.f2.6.0.5.13.ord,"force")
LG.f2.6.0.5.14.ord.all <- make_seq(LG.f2.6.0.5.14.ord,"force")
LG.f2.6.0.5.15.ord.all <- make_seq(LG.f2.6.0.5.15.ord,"force")
LG.f2.6.0.5.16.ord.all <- make_seq(LG.f2.6.0.5.16.ord,"force")
LG.f2.6.0.5.17.ord.all <- make_seq(LG.f2.6.0.5.17.ord,"force")
LG.f2.6.0.5.18.ord.all <- make_seq(LG.f2.6.0.5.18.ord,"force")
LG.f2.6.0.5.19.ord.all <- make_seq(LG.f2.6.0.5.19.ord,"force")
LG.f2.6.0.5.20.ord.all <- make_seq(LG.f2.6.0.5.20.ord,"force")
LG.f2.6.0.5.21.ord.all <- make_seq(LG.f2.6.0.5.21.ord,"force")
LG.f2.6.0.5.22.ord.all <- make_seq(LG.f2.6.0.5.22.ord,"force")
LG.f2.6.0.5.23.ord.all <- make_seq(LG.f2.6.0.5.23.ord,"force")
LG.f2.6.0.5.24.ord.all <- make_seq(LG.f2.6.0.5.24.ord,"force")
LG.f2.6.0.5.25.ord.all <- make_seq(LG.f2.6.0.5.25.ord,"force")
LG.f2.6.0.5.26.ord.all <- make_seq(LG.f2.6.0.5.26.ord,"force")
LG.f2.6.0.5.27.ord.all <- make_seq(LG.f2.6.0.5.27.ord,"force")
LG.f2.6.0.5.28.ord.all <- make_seq(LG.f2.6.0.5.28.ord,"force")
LG.f2.6.0.5.29.ord.all <- make_seq(LG.f2.6.0.5.29.ord,"force")
LG.f2.6.0.5.30.ord.all <- make_seq(LG.f2.6.0.5.30.ord,"force")
LG.f2.6.0.5.31.ord.all <- make_seq(LG.f2.6.0.5.31.ord,"force")
LG.f2.6.0.5.32.ord.all <- make_seq(LG.f2.6.0.5.32.ord,"force")

```

Drawing the genetic map

```{r}
Map.6.0.5.ord.safe <- list(
LG.f2.6.0.5.1.ord.safe, 
LG.f2.6.0.5.2.ord.safe, 
LG.f2.6.0.5.3.ord.safe, 
LG.f2.6.0.5.4.ord.safe, 
LG.f2.6.0.5.5.ord.safe, 
LG.f2.6.0.5.6.ord.safe, 
LG.f2.6.0.5.7.ord.safe, 
LG.f2.6.0.5.8.ord.safe, 
LG.f2.6.0.5.9.ord.safe, 
LG.f2.6.0.5.10.ord.safe,
LG.f2.6.0.5.11.ord.safe,
LG.f2.6.0.5.12.ord.safe,
LG.f2.6.0.5.13.ord.safe,
LG.f2.6.0.5.14.ord.safe,
LG.f2.6.0.5.15.ord.safe,
LG.f2.6.0.5.16.ord.safe,
LG.f2.6.0.5.17.ord.safe,
LG.f2.6.0.5.18.ord.safe,
LG.f2.6.0.5.19.ord.safe,
LG.f2.6.0.5.20.ord.safe,
LG.f2.6.0.5.21.ord.safe,
LG.f2.6.0.5.22.ord.safe,
LG.f2.6.0.5.23.ord.safe,
LG.f2.6.0.5.24.ord.safe,
LG.f2.6.0.5.25.ord.safe,
LG.f2.6.0.5.26.ord.safe,
LG.f2.6.0.5.27.ord.safe,
LG.f2.6.0.5.28.ord.safe,
LG.f2.6.0.5.29.ord.safe,
LG.f2.6.0.5.30.ord.safe,
LG.f2.6.0.5.31.ord.safe,
LG.f2.6.0.5.32.ord.safe)

Map.6.0.5.ord.all <- list(
LG.f2.6.0.5.1.ord.all, 
LG.f2.6.0.5.2.ord.all, 
LG.f2.6.0.5.3.ord.all, 
LG.f2.6.0.5.4.ord.all, 
LG.f2.6.0.5.5.ord.all, 
LG.f2.6.0.5.6.ord.all, 
LG.f2.6.0.5.7.ord.all, 
LG.f2.6.0.5.8.ord.all, 
LG.f2.6.0.5.9.ord.all, 
LG.f2.6.0.5.10.ord.all,
LG.f2.6.0.5.11.ord.all,
LG.f2.6.0.5.12.ord.all,
LG.f2.6.0.5.13.ord.all,
LG.f2.6.0.5.14.ord.all,
LG.f2.6.0.5.15.ord.all,
LG.f2.6.0.5.16.ord.all,
LG.f2.6.0.5.17.ord.all,
LG.f2.6.0.5.18.ord.all,
LG.f2.6.0.5.19.ord.all,
LG.f2.6.0.5.20.ord.all,
LG.f2.6.0.5.21.ord.all,
LG.f2.6.0.5.22.ord.all,
LG.f2.6.0.5.23.ord.all,
LG.f2.6.0.5.24.ord.all,
LG.f2.6.0.5.25.ord.all,
LG.f2.6.0.5.26.ord.all,
LG.f2.6.0.5.27.ord.all,
LG.f2.6.0.5.28.ord.all,
LG.f2.6.0.5.29.ord.all,
LG.f2.6.0.5.30.ord.all,
LG.f2.6.0.5.31.ord.all,
LG.f2.6.0.5.32.ord.all)

draw_map(Map.6.0.5.ord.safe, names= TRUE, grid=TRUE, cex.mrk=0.3)

draw_map(Map.6.0.5.ord.all, names= TRUE, grid=TRUE, cex.mrk=0.3)

```

Linage group 2 has more of 50 cM between the majority of the markers and the remaining 3

```{r}

LG.f2.6.0.5.2.ord.safe2 <- LG.f2.6.0.5.2.ord.safe
LG.f2.6.0.5.2.ord.safe2$seq.rf <- LG.f2.6.0.5.2.ord.safe$seq.rf[-c(1:3)]
LG.f2.6.0.5.2.ord.safe2$seq.phases <- LG.f2.6.0.5.2.ord.safe$seq.phases[-c(1:3)]
LG.f2.6.0.5.2.ord.safe2$seq.num <- LG.f2.6.0.5.2.ord.safe$seq.num[-c(1:3)]
LG.f2.6.0.5.2.ord.safe2

Map.6.0.5.ord.safe2 <- list(
LG.f2.6.0.5.1.ord.safe, 
LG.f2.6.0.5.2.ord.safe2, 
LG.f2.6.0.5.3.ord.safe, 
LG.f2.6.0.5.4.ord.safe, 
LG.f2.6.0.5.5.ord.safe, 
LG.f2.6.0.5.6.ord.safe, 
LG.f2.6.0.5.7.ord.safe, 
LG.f2.6.0.5.8.ord.safe, 
LG.f2.6.0.5.9.ord.safe, 
LG.f2.6.0.5.10.ord.safe,
LG.f2.6.0.5.11.ord.safe,
LG.f2.6.0.5.12.ord.safe,
LG.f2.6.0.5.13.ord.safe,
LG.f2.6.0.5.14.ord.safe,
LG.f2.6.0.5.15.ord.safe,
LG.f2.6.0.5.16.ord.safe,
LG.f2.6.0.5.17.ord.safe,
LG.f2.6.0.5.18.ord.safe,
LG.f2.6.0.5.19.ord.safe,
LG.f2.6.0.5.20.ord.safe,
LG.f2.6.0.5.21.ord.safe,
LG.f2.6.0.5.22.ord.safe,
LG.f2.6.0.5.23.ord.safe,
LG.f2.6.0.5.24.ord.safe,
LG.f2.6.0.5.25.ord.safe,
LG.f2.6.0.5.26.ord.safe,
LG.f2.6.0.5.27.ord.safe,
LG.f2.6.0.5.28.ord.safe,
LG.f2.6.0.5.29.ord.safe,
LG.f2.6.0.5.30.ord.safe,
LG.f2.6.0.5.31.ord.safe,
LG.f2.6.0.5.32.ord.safe)

draw.map(Map.6.0.5.ord.safe2, names= TRUE, grid=TRUE, cex.mrk=0.3)

```

Linage group 24 has more of 50 cM between the majority of the markers and the remaining 8

```{r}

LG.f2.6.0.5.24.ord.safe2 <- LG.f2.6.0.5.24.ord.safe
LG.f2.6.0.5.24.ord.safe2$seq.rf <- LG.f2.6.0.5.24.ord.safe$seq.rf[-c(1:8)]
LG.f2.6.0.5.24.ord.safe2$seq.phases <- LG.f2.6.0.5.24.ord.safe$seq.phases[-c(1:8)]
LG.f2.6.0.5.24.ord.safe2$seq.num <- LG.f2.6.0.5.24.ord.safe$seq.num[-c(1:8)]
LG.f2.6.0.5.24.ord.safe2

Map.6.0.5.ord.safe3 <- list(
LG.f2.6.0.5.1.ord.safe, 
LG.f2.6.0.5.2.ord.safe2, 
LG.f2.6.0.5.3.ord.safe, 
LG.f2.6.0.5.4.ord.safe, 
LG.f2.6.0.5.5.ord.safe, 
LG.f2.6.0.5.6.ord.safe, 
LG.f2.6.0.5.7.ord.safe, 
LG.f2.6.0.5.8.ord.safe, 
LG.f2.6.0.5.9.ord.safe, 
LG.f2.6.0.5.10.ord.safe,
LG.f2.6.0.5.11.ord.safe,
LG.f2.6.0.5.12.ord.safe,
LG.f2.6.0.5.13.ord.safe,
LG.f2.6.0.5.14.ord.safe,
LG.f2.6.0.5.15.ord.safe,
LG.f2.6.0.5.16.ord.safe,
LG.f2.6.0.5.17.ord.safe,
LG.f2.6.0.5.18.ord.safe,
LG.f2.6.0.5.19.ord.safe,
LG.f2.6.0.5.20.ord.safe,
LG.f2.6.0.5.21.ord.safe,
LG.f2.6.0.5.22.ord.safe,
LG.f2.6.0.5.23.ord.safe,
LG.f2.6.0.5.24.ord.safe2,
LG.f2.6.0.5.25.ord.safe,
LG.f2.6.0.5.26.ord.safe,
LG.f2.6.0.5.27.ord.safe,
LG.f2.6.0.5.28.ord.safe,
LG.f2.6.0.5.29.ord.safe,
LG.f2.6.0.5.30.ord.safe,
LG.f2.6.0.5.31.ord.safe,
LG.f2.6.0.5.32.ord.safe)

draw.map(Map.6.0.5.ord.safe3, names= TRUE, grid=TRUE, cex.mrk=0.3)

```

Finally, the linkage group 25 have over 40 cM between the majority of the markers and the last one


```{r}

LG.f2.6.0.5.25.ord.safe2 <- LG.f2.6.0.5.25.ord.safe
LG.f2.6.0.5.25.ord.safe2$seq.num <- LG.f2.6.0.5.25.ord.safe$seq.num[1:19]
LG.f2.6.0.5.25.ord.safe2$seq.rf <- LG.f2.6.0.5.25.ord.safe$seq.rf[1:18]
LG.f2.6.0.5.25.ord.safe2$seq.phases <- LG.f2.6.0.5.25.ord.safe$seq.phases[1:18]
LG.f2.6.0.5.25.ord.safe2

Map.6.0.5.ord.safe4 <- list(
LG.f2.6.0.5.1.ord.safe, 
LG.f2.6.0.5.2.ord.safe2, 
LG.f2.6.0.5.3.ord.safe, 
LG.f2.6.0.5.4.ord.safe, 
LG.f2.6.0.5.5.ord.safe, 
LG.f2.6.0.5.6.ord.safe, 
LG.f2.6.0.5.7.ord.safe, 
LG.f2.6.0.5.8.ord.safe, 
LG.f2.6.0.5.9.ord.safe, 
LG.f2.6.0.5.10.ord.safe,
LG.f2.6.0.5.11.ord.safe,
LG.f2.6.0.5.12.ord.safe,
LG.f2.6.0.5.13.ord.safe,
LG.f2.6.0.5.14.ord.safe,
LG.f2.6.0.5.15.ord.safe,
LG.f2.6.0.5.16.ord.safe,
LG.f2.6.0.5.17.ord.safe,
LG.f2.6.0.5.18.ord.safe,
LG.f2.6.0.5.19.ord.safe,
LG.f2.6.0.5.20.ord.safe,
LG.f2.6.0.5.21.ord.safe,
LG.f2.6.0.5.22.ord.safe,
LG.f2.6.0.5.23.ord.safe,
LG.f2.6.0.5.24.ord.safe2,
LG.f2.6.0.5.25.ord.safe2,
LG.f2.6.0.5.26.ord.safe,
LG.f2.6.0.5.27.ord.safe,
LG.f2.6.0.5.28.ord.safe,
LG.f2.6.0.5.29.ord.safe,
LG.f2.6.0.5.30.ord.safe,
LG.f2.6.0.5.31.ord.safe,
LG.f2.6.0.5.32.ord.safe)

draw.map(Map.6.0.5.ord.safe4, names= TRUE, grid=TRUE, cex.mrk=0.3)

```

This is our final map!

Now we are going to look for linkage groups with a higher number than markers under segregation distortion that what would be expected by chance.
But first we will check wether or not there is a correlation between missing data and segregation distortion.

```{r}

mydata <- read.csv(file="permutations1.csv")
mydata
x2 <- mydata[,2]
missingdata <- mydata[,3]
summary(lm(x2 ~ missingdata))
plot(x2 ~ missingdata, main="", xlab = "Number of individuals missing the marker", ylab = "Segregation distortion (X-square)")


LG1 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.1.ord.all$seq.num),]
LG1
nrow(LG1)
LG1.per <- matrix(0, nrow=1000, ncol = nrow(LG1))
for (j in 1:1000) LG1.per[j,] <- sample(x2, nrow(LG1), replace = FALSE, prob = NULL)
histLG1 <- vector()
for (i in 1:1000) histLG1[i] <- length(LG1.per[i,][LG1.per[i,]>5.991])
hist(histLG1)
abline(v=length(LG1[,2][LG1[,2]>5.991]),col="red")
length(LG1[,2][LG1[,2]>13.5])

LG2 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.2.ord.all$seq.num),]
LG2
nrow(LG2)
LG2.per <- matrix(0, nrow=1000, ncol = nrow(LG2))
for (j in 1:1000) LG2.per[j,] <- sample(x2, nrow(LG2), replace = FALSE, prob = NULL)
histLG2 <- vector()
for (i in 1:1000) histLG2[i] <- length(LG2.per[i,][LG2.per[i,]>5.991])
hist(histLG2)
abline(v=length(LG2[,2][LG2[,2]>5.991]),col="red")
length(LG2[,2][LG2[,2]>13.5])

LG3 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.3.ord.all$seq.num),]
LG3
nrow(LG3)
LG3.per <- matrix(0, nrow=1000, ncol = nrow(LG3))
for (j in 1:1000) LG3.per[j,] <- sample(x2, nrow(LG3), replace = FALSE, prob = NULL)
histLG3 <- vector()
for (i in 1:1000) histLG3[i] <- length(LG3.per[i,][LG3.per[i,]>5.991])
hist(histLG3)
abline(v=length(LG3[,2][LG3[,2]>5.991]),col="red")
length(LG3[,2][LG3[,2]>13.5])


LG4 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.4.ord.all$seq.num),]
LG4
nrow(LG4)
LG4.per <- matrix(0, nrow=1000, ncol = nrow(LG4))
for (j in 1:1000) LG4.per[j,] <- sample(x2, nrow(LG4), replace = FALSE, prob = NULL)
histLG4 <- vector()
for (i in 1:1000) histLG4[i] <- length(LG4.per[i,][LG4.per[i,]>5.991])
hist(histLG4, xlim = c(0,60))
abline(v=length(LG4[,2][LG4[,2]>5.991]),col="red")
length(LG4[,2][LG4[,2]>13.5])

LG5 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.5.ord.all$seq.num),]
LG5
nrow(LG5)
LG5.per <- matrix(0, nrow=1000, ncol = nrow(LG5))
for (j in 1:1000) LG5.per[j,] <- sample(x2, nrow(LG5), replace = FALSE, prob = NULL)
histLG5 <- vector()
for (i in 1:1000) histLG5[i] <- length(LG5.per[i,][LG5.per[i,]>5.991])
hist(histLG5)
abline(v=length(LG5[,2][LG5[,2]>5.991]),col="red")
length(LG5[,2][LG5[,2]>13.5])


LG6 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.6.ord.all$seq.num),]
LG6
nrow(LG6)
LG6.per <- matrix(0, nrow=1000, ncol = nrow(LG6))
for (j in 1:1000) LG6.per[j,] <- sample(x2, nrow(LG6), replace = FALSE, prob = NULL)
histLG6 <- vector()
for (i in 1:1000) histLG6[i] <- length(LG6.per[i,][LG6.per[i,]>5.991])
hist(histLG6)
abline(v=length(LG6[,2][LG6[,2]>5.991]),col="red")
length(LG6[,2][LG6[,2]>13.5])


LG7 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.7.ord.all$seq.num),]
LG7
nrow(LG7)
LG7.per <- matrix(0, nrow=1000, ncol = nrow(LG7))
for (j in 1:1000) LG7.per[j,] <- sample(x2, nrow(LG7), replace = FALSE, prob = NULL)
histLG7 <- vector()
for (i in 1:1000) histLG7[i] <- length(LG7.per[i,][LG7.per[i,]>5.991])
hist(histLG7)
abline(v=length(LG7[,2][LG7[,2]>5.991]),col="red")
length(LG7[,2][LG7[,2]>13.5])

LG8 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.8.ord.all$seq.num),]
LG8
nrow(LG8)
LG8.per <- matrix(0, nrow=1000, ncol = nrow(LG8))
for (j in 1:1000) LG8.per[j,] <- sample(x2, nrow(LG8), replace = FALSE, prob = NULL)
histLG8 <- vector()
for (i in 1:1000) histLG8[i] <- length(LG8.per[i,][LG8.per[i,]>5.991])
hist(histLG8)
abline(v=length(LG8[,2][LG8[,2]>5.991]),col="red")
length(LG8[,2][LG8[,2]>13.5])

LG9 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.9.ord.all$seq.num),]
LG9
nrow(LG9)
LG9.per <- matrix(0, nrow=1000, ncol = nrow(LG9))
for (j in 1:1000) LG9.per[j,] <- sample(x2, nrow(LG9), replace = FALSE, prob = NULL)
histLG9 <- vector()
for (i in 1:1000) histLG9[i] <- length(LG9.per[i,][LG9.per[i,]>5.991])
hist(histLG9, xlim = c(0,30))
abline(v=length(LG9[,2][LG9[,2]>5.991]),col="red")
length(LG9[,2][LG9[,2]>13.5])

LG10 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.10.ord.all$seq.num),]
LG10
nrow(LG10)
LG10.per <- matrix(0, nrow=1000, ncol = nrow(LG10))
for (j in 1:1000) LG10.per[j,] <- sample(x2, nrow(LG10), replace = FALSE, prob = NULL)
histLG10 <- vector()
for (i in 1:1000) histLG10[i] <- length(LG10.per[i,][LG10.per[i,]>5.991])
hist(histLG10)
abline(v=length(LG10[,2][LG10[,2]>5.991]),col="red")
length(LG10[,2][LG10[,2]>13.5])

LG11 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.11.ord.all$seq.num),]
LG11
nrow(LG11)
LG11.per <- matrix(0, nrow=1000, ncol = nrow(LG11))
for (j in 1:1000) LG11.per[j,] <- sample(x2, nrow(LG11), replace = FALSE, prob = NULL)
histLG11 <- vector()
for (i in 1:1000) histLG11[i] <- length(LG11.per[i,][LG11.per[i,]>5.991])
hist(histLG11)
abline(v=length(LG11[,2][LG11[,2]>5.991]),col="red")
length(LG11[,2][LG11[,2]>13.5])

LG12 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.12.ord.all$seq.num),]
LG12
nrow(LG12)
LG12.per <- matrix(0, nrow=1000, ncol = nrow(LG12))
for (j in 1:1000) LG12.per[j,] <- sample(x2, nrow(LG12), replace = FALSE, prob = NULL)
histLG12 <- vector()
for (i in 1:1000) histLG12[i] <- length(LG12.per[i,][LG12.per[i,]>5.991])
hist(histLG12)
abline(v=length(LG12[,2][LG12[,2]>5.991]),col="red")
length(LG12[,2][LG12[,2]>13.5])

LG13 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.13.ord.all$seq.num),]
LG13
nrow(LG13)
LG13.per <- matrix(0, nrow=1000, ncol = nrow(LG13))
for (j in 1:1000) LG13.per[j,] <- sample(x2, nrow(LG13), replace = FALSE, prob = NULL)
histLG13 <- vector()
for (i in 1:1000) histLG13[i] <- length(LG13.per[i,][LG13.per[i,]>5.991])
hist(histLG13, xlim = c(2,21))
abline(v=length(LG13[,2][LG13[,2]>5.991]),col="red")
length(LG13[,2][LG13[,2]>13.5])

LG14 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.14.ord.all$seq.num),]
LG14
nrow(LG14)
LG14.per <- matrix(0, nrow=1000, ncol = nrow(LG14))
for (j in 1:1000) LG14.per[j,] <- sample(x2, nrow(LG14), replace = FALSE, prob = NULL)
histLG14 <- vector()
for (i in 1:1000) histLG14[i] <- length(LG14.per[i,][LG14.per[i,]>5.991])
hist(histLG14)
abline(v=length(LG14[,2][LG14[,2]>5.991]),col="red")
length(LG14[,2][LG14[,2]>13.5])

LG15 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.15.ord.all$seq.num),]
LG15
nrow(LG15)
LG15.per <- matrix(0, nrow=1000, ncol = nrow(LG15))
for (j in 1:1000) LG15.per[j,] <- sample(x2, nrow(LG15), replace = FALSE, prob = NULL)
histLG15 <- vector()
for (i in 1:1000) histLG15[i] <- length(LG15.per[i,][LG15.per[i,]>5.991])
hist(histLG15)
abline(v=length(LG15[,2][LG15[,2]>5.991]),col="red")
length(LG15[,2][LG15[,2]>13.5])

LG16 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.16.ord.all$seq.num),]
LG16
nrow(LG16)
LG16.per <- matrix(0, nrow=1000, ncol = nrow(LG16))
for (j in 1:1000) LG16.per[j,] <- sample(x2, nrow(LG16), replace = FALSE, prob = NULL)
histLG16 <- vector()
for (i in 1:1000) histLG16[i] <- length(LG16.per[i,][LG16.per[i,]>5.991])
hist(histLG16)
abline(v=length(LG16[,2][LG16[,2]>5.991]),col="red")
length(LG16[,2][LG16[,2]>13.5])

LG17 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.17.ord.all$seq.num),]
LG17
nrow(LG17)
LG17.per <- matrix(0, nrow=1000, ncol = nrow(LG17))
for (j in 1:1000) LG17.per[j,] <- sample(x2, nrow(LG17), replace = FALSE, prob = NULL)
histLG17 <- vector()
for (i in 1:1000) histLG17[i] <- length(LG17.per[i,][LG17.per[i,]>5.991])
hist(histLG17, xlim = c(5,50))
abline(v=length(LG17[,2][LG17[,2]>5.991]),col="red")
length(LG17[,2][LG17[,2]>13.5])

LG18 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.18.ord.all$seq.num),]
LG18
nrow(LG18)
LG18.per <- matrix(0, nrow=1000, ncol = nrow(LG18))
for (j in 1:1000) LG18.per[j,] <- sample(x2, nrow(LG18), replace = FALSE, prob = NULL)
histLG18 <- vector()
for (i in 1:1000) histLG18[i] <- length(LG18.per[i,][LG18.per[i,]>5.991])
hist(histLG18)
abline(v=length(LG18[,2][LG18[,2]>5.991]),col="red")
length(LG18[,2][LG18[,2]>13.5])

LG19 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.19.ord.all$seq.num),]
LG19
nrow(LG19)
LG19.per <- matrix(0, nrow=1000, ncol = nrow(LG19))
for (j in 1:1000) LG19.per[j,] <- sample(x2, nrow(LG19), replace = FALSE, prob = NULL)
histLG19 <- vector()
for (i in 1:1000) histLG19[i] <- length(LG19.per[i,][LG19.per[i,]>5.991])
hist(histLG19)
abline(v=length(LG19[,2][LG19[,2]>5.991]),col="red")
length(LG19[,2][LG19[,2]>13.5])

LG20 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.20.ord.all$seq.num),]
LG20
nrow(LG20)
LG20.per <- matrix(0, nrow=1000, ncol = nrow(LG20))
for (j in 1:1000) LG20.per[j,] <- sample(x2, nrow(LG20), replace = FALSE, prob = NULL)
histLG20 <- vector()
for (i in 1:1000) histLG20[i] <- length(LG20.per[i,][LG20.per[i,]>5.991])
hist(histLG20)
abline(v=length(LG20[,2][LG20[,2]>5.991]),col="red")
length(LG20[,2][LG20[,2]>13.5])

LG21 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.21.ord.all$seq.num),]
LG21
nrow(LG21)
LG21.per <- matrix(0, nrow=1000, ncol = nrow(LG21))
for (j in 1:1000) LG21.per[j,] <- sample(x2, nrow(LG21), replace = FALSE, prob = NULL)
histLG21 <- vector()
for (i in 1:1000) histLG21[i] <- length(LG21.per[i,][LG21.per[i,]>5.991])
hist(histLG21)
abline(v=length(LG21[,2][LG21[,2]>5.991]),col="red")
length(LG21[,2][LG21[,2]>13.5])

LG22 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.22.ord.all$seq.num),]
LG22
nrow(LG22)
LG22.per <- matrix(0, nrow=1000, ncol = nrow(LG22))
for (j in 1:1000) LG22.per[j,] <- sample(x2, nrow(LG22), replace = FALSE, prob = NULL)
histLG22 <- vector()
for (i in 1:1000) histLG22[i] <- length(LG22.per[i,][LG22.per[i,]>5.991])
hist(histLG22)
abline(v=length(LG22[,2][LG22[,2]>5.991]),col="red")
length(LG22[,2][LG22[,2]>13.5])

LG23 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.23.ord.all$seq.num),]
LG23
nrow(LG23)
LG23.per <- matrix(0, nrow=1000, ncol = nrow(LG23))
for (j in 1:1000) LG23.per[j,] <- sample(x2, nrow(LG23), replace = FALSE, prob = NULL)
histLG23 <- vector()
for (i in 1:1000) histLG23[i] <- length(LG23.per[i,][LG23.per[i,]>5.991])
hist(histLG23, xlim=c(0,13))
abline(v=length(LG23[,2][LG23[,2]>5.991]),col="red")
length(LG23[,2][LG23[,2]>13.5])

LG24 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.24.ord.all$seq.num),]
LG24
nrow(LG24)
LG24.per <- matrix(0, nrow=1000, ncol = nrow(LG24))
for (j in 1:1000) LG24.per[j,] <- sample(x2, nrow(LG24), replace = FALSE, prob = NULL)
histLG24 <- vector()
for (i in 1:1000) histLG24[i] <- length(LG24.per[i,][LG24.per[i,]>5.991])
hist(histLG24)
abline(v=length(LG24[,2][LG24[,2]>5.991]),col="red")
length(LG24[,2][LG24[,2]>13.5])

LG25 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.25.ord.all$seq.num),]
LG25
nrow(LG25)
LG25.per <- matrix(0, nrow=1000, ncol = nrow(LG25))
for (j in 1:1000) LG25.per[j,] <- sample(x2, nrow(LG25), replace = FALSE, prob = NULL)
histLG25 <- vector()
for (i in 1:1000) histLG25[i] <- length(LG25.per[i,][LG25.per[i,]>5.991])
hist(histLG25)
abline(v=length(LG25[,2][LG25[,2]>5.991]),col="red")
length(LG25[,2][LG25[,2]>13.5])

LG26 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.26.ord.all$seq.num),]
LG26
nrow(LG26)
LG26.per <- matrix(0, nrow=1000, ncol = nrow(LG26))
for (j in 1:1000) LG26.per[j,] <- sample(x2, nrow(LG26), replace = FALSE, prob = NULL)
histLG26 <- vector()
for (i in 1:1000) histLG26[i] <- length(LG26.per[i,][LG26.per[i,]>5.991])
hist(histLG26)
abline(v=length(LG26[,2][LG26[,2]>5.991]),col="red")
length(LG26[,2][LG26[,2]>13.5])

LG27 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.27.ord.all$seq.num),]
LG27
nrow(LG27)
LG27.per <- matrix(0, nrow=1000, ncol = nrow(LG27))
for (j in 1:1000) LG27.per[j,] <- sample(x2, nrow(LG27), replace = FALSE, prob = NULL)
histLG27 <- vector()
for (i in 1:1000) histLG27[i] <- length(LG27.per[i,][LG27.per[i,]>5.991])
hist(histLG27)
abline(v=length(LG27[,2][LG27[,2]>5.991]),col="red")
length(LG27[,2][LG27[,2]>13.5])

LG28 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.28.ord.all$seq.num),]
LG28
nrow(LG28)
LG28.per <- matrix(0, nrow=1000, ncol = nrow(LG28))
for (j in 1:1000) LG28.per[j,] <- sample(x2, nrow(LG28), replace = FALSE, prob = NULL)
histLG28 <- vector()
for (i in 1:1000) histLG28[i] <- length(LG28.per[i,][LG28.per[i,]>5.991])
hist(histLG28)
abline(v=length(LG28[,2][LG28[,2]>5.991]),col="red")
length(LG28[,2][LG28[,2]>13.5])

LG29 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.29.ord.all$seq.num),]
LG29
nrow(LG29)
LG29.per <- matrix(0, nrow=1000, ncol = nrow(LG29))
for (j in 1:1000) LG29.per[j,] <- sample(x2, nrow(LG29), replace = FALSE, prob = NULL)
histLG29 <- vector()
for (i in 1:1000) histLG29[i] <- length(LG29.per[i,][LG29.per[i,]>5.991])
hist(histLG29)
abline(v=length(LG29[,2][LG29[,2]>5.991]),col="red")
length(LG29[,2][LG29[,2]>13.5])

LG30 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.30.ord.all$seq.num),]
LG30
nrow(LG30)
LG30.per <- matrix(0, nrow=1000, ncol = nrow(LG30))
for (j in 1:1000) LG30.per[j,] <- sample(x2, nrow(LG30), replace = FALSE, prob = NULL)
histLG30 <- vector()
for (i in 1:1000) histLG30[i] <- length(LG30.per[i,][LG30.per[i,]>5.991])
hist(histLG30)
abline(v=length(LG30[,2][LG30[,2]>5.991]),col="red")
length(LG30[,2][LG30[,2]>13.5])

LG31 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.31.ord.all$seq.num),]
LG31
nrow(LG31)
LG31.per <- matrix(0, nrow=1000, ncol = nrow(LG31))
for (j in 1:1000) LG31.per[j,] <- sample(x2, nrow(LG31), replace = FALSE, prob = NULL)
histLG31 <- vector()
for (i in 1:1000) histLG31[i] <- length(LG31.per[i,][LG31.per[i,]>5.991])
hist(histLG31)
abline(v=length(LG31[,2][LG31[,2]>5.991]),col="red")
length(LG31[,2][LG31[,2]>13.5])

LG32 <- mydata[intersect(mydata[,4],LG.f2.6.0.5.32.ord.all$seq.num),]
LG32
nrow(LG32)
LG32.per <- matrix(0, nrow=1000, ncol = nrow(LG32))
for (j in 1:1000) LG32.per[j,] <- sample(x2, nrow(LG32), replace = FALSE, prob = NULL)
histLG32 <- vector()
for (i in 1:1000) histLG32[i] <- length(LG32.per[i,][LG32.per[i,]>5.991])
hist(histLG32)
abline(v=length(LG32[,2][LG32[,2]>5.991]),col="red")
length(LG32[,2][LG32[,2]>13.5])

```

Linkage groups 13, 17 and 31 have more markers under segregation distortion that expected by chance

Now we are going to check whether or not those markers under segregation distortion are grouped together within the linkage groups.

And first, we will check again whether or not for these specific linkage groups there is any king of correlation between missing data and segregation distortion.

```{r}

x2 <- LG31[,2]
missingdata <- LG31[,3]
summary(lm(x2 ~ missingdata))
plot(x2 ~ missingdata, main="", xlab = "Number of individuals missing the marker", ylab = "Segregation distortion (X-square)")

x2 <- LG17[,2]
missingdata <- LG17[,3]
summary(lm(x2 ~ missingdata))
plot(x2 ~ missingdata, main="", xlab = "Number of individuals missing the marker", ylab = "Segregation distortion (X-square)")

x2 <- LG13[,2]
missingdata <- LG13[,3]
summary(lm(x2 ~ missingdata))
plot(x2 ~ missingdata, main="", xlab = "Number of individuals missing the marker", ylab = "Segregation distortion (X-square)")

LG13.pos <- read.csv("LG13.csv")
setdiff(LG13.pos[,1],LG13[,4])
setdiff(LG13.pos[,2],LG13[,1])

library(ggplot2)
LG13.pos[,4] <- LG13[,2][match(LG13.pos[,2],LG13[,1])]
names(LG13.pos)[4] <- "CHISQUARE"
p13 <- ggplot(LG13.pos, aes(POSITION))+
  geom_line(data=subset(LG13.pos),aes(y=CHISQUARE),col="black", linetype="dotted")+
  geom_point(data=subset(LG13.pos),aes(y=CHISQUARE),col="black")+
  scale_y_continuous(limits = c(0, 20))+
  geom_ribbon(data=subset(LG13.pos),aes(ymin=0,ymax=5.991),alpha=0.5,fill="grey")+
  geom_errorbar(data=subset(LG13.pos),aes(ymin=CHISQUARE,ymax=CHISQUARE),width=1)+
  theme_bw(base_size=20)+
  xlab('Distance (CentiMorgan)') +
  ylab('SD (CHISQUARE)')
p13

LG31.pos <- read.csv("LG31.csv")
setdiff(LG31.pos[,1],LG31[,4])
setdiff(LG31.pos[,2],LG31[,1])

LG31.pos[,4] <- LG31[,2][match(LG31.pos[,2],LG31[,1])]
names(LG31.pos)[4] <- "CHISQUARE"
p31 <- ggplot(LG31.pos, aes(POSITION))+
  geom_line(data=subset(LG31.pos),aes(y=CHISQUARE),col="black", linetype="dotted")+
  geom_point(data=subset(LG31.pos),aes(y=CHISQUARE),col="black")+
  scale_y_continuous(limits = c(0, 60))+
  geom_ribbon(data=subset(LG31.pos),aes(ymin=0,ymax=5.991),alpha=0.5,fill="grey")+
  geom_errorbar(data=subset(LG31.pos),aes(ymin=CHISQUARE,ymax=CHISQUARE),width=1)+
  theme_bw(base_size=20)+
  xlab('Distance (CentiMorgan)') +
  ylab('SD (CHISQUARE)')
p31


LG17.pos <- read.csv("LG17.csv")
setdiff(LG17.pos[,1],LG17[,4])
setdiff(LG17.pos[,2],LG17[,1])

LG17.pos[,4] <- LG17[,2][match(LG17.pos[,2],LG17[,1])]
names(LG17.pos)[4] <- "CHISQUARE"
p17 <- ggplot(LG17.pos, aes(POSITION))+
  geom_line(data=subset(LG17.pos),aes(y=CHISQUARE),col="black", linetype="dotted")+
  geom_point(data=subset(LG17.pos),aes(y=CHISQUARE),col="black")+
  scale_y_continuous(limits = c(0, 13.5))+
  geom_ribbon(data=subset(LG17.pos),aes(ymin=0,ymax=5.991),alpha=0.5,fill="grey")+
  geom_errorbar(data=subset(LG17.pos),aes(ymin=CHISQUARE,ymax=CHISQUARE),width=1)+
  theme_bw(base_size=20)+
  xlab('Distance (CentiMorgan)') +
  ylab('SD (CHISQUARE)')
p17

library(adehabitat)
wawotest(as.numeric(LG31$CHISQUARE > 5.991))
wawotest(as.numeric(LG17$CHISQUARE > 5.991))
wawotest(as.numeric(LG13$CHISQUARE > 5.991))
```

Now we are going to repeat the last analysis for LG17 and LG13 but excluding the loci that are not safely located

```{r}
LG13.red.pos <- read.csv("LG13.red.csv")
setdiff(LG13.red.pos[,1],LG13[,4])
setdiff(LG13.red.pos[,2],LG13[,1])

library(ggplot2)
LG13.red.pos[,4] <- LG13[,2][match(LG13.red.pos[,2],LG13[,1])]
names(LG13.red.pos)[4] <- "CHISQUARE"
p13.red <- ggplot(LG13.red.pos, aes(POSITION))+
  geom_line(data=subset(LG13.red.pos),aes(y=CHISQUARE),col="black", linetype="dotted")+
  geom_point(data=subset(LG13.red.pos),aes(y=CHISQUARE),col="black")+
  scale_y_continuous(limits = c(0, 20))+
  geom_ribbon(data=subset(LG13.red.pos),aes(ymin=0,ymax=5.991),alpha=0.5,fill="grey")+
  geom_errorbar(data=subset(LG13.red.pos),aes(ymin=CHISQUARE,ymax=CHISQUARE),width=1)+
  theme_bw(base_size=20)+
  xlab('Distance (CentiMorgan)') +
  ylab('SD (CHISQUARE)')
p13.red


LG17.red.pos <- read.csv("LG17.red.csv")
setdiff(LG17.red.pos[,1],LG17[,4])
setdiff(LG17.red.pos[,2],LG17[,1])

LG17.red.pos[,4] <- LG17[,2][match(LG17.red.pos[,2],LG17[,1])]
names(LG17.red.pos)[4] <- "CHISQUARE"
p17.red <- ggplot(LG17.red.pos, aes(POSITION))+
  geom_line(data=subset(LG17.red.pos),aes(y=CHISQUARE),col="black", linetype="dotted")+
  geom_point(data=subset(LG17.red.pos),aes(y=CHISQUARE),col="black")+
  scale_y_continuous(limits = c(0, 13.5))+
  geom_ribbon(data=subset(LG17.red.pos),aes(ymin=0,ymax=5.991),alpha=0.5,fill="grey")+
  geom_errorbar(data=subset(LG17.red.pos),aes(ymin=CHISQUARE,ymax=CHISQUARE),width=1)+
  theme_bw(base_size=20)+
  xlab('Distance (CentiMorgan)') +
  ylab('SD (CHISQUARE)')
p17.red

library(adehabitat)
wawotest(as.numeric(LG17.red.pos$CHISQUARE > 5.991))
wawotest(as.numeric(LG13.red.pos$CHISQUARE > 5.991))

```

#########################################################
AFTER FIRST REVIEW
########################################################
We are going to repeat the process but including the 85 loci under severe segregation distortion

First, we load the package onemap and import the data set

```{r}

library (onemap)

f2.onemap.sd <- read_mapmaker(file = "onemap.f2.sd.txt")

```

Second, we assign markers to linkage groups

```{r}
twopts.sd <- rf_2pts(f2.onemap.sd, LOD=3, max.rf=0.5)
mark.all.sd <- make_seq(twopts.sd, "all")
LGs.f2.6.0.5.sd <- group(mark.all.sd, LOD = 6, max.rf = 0.5)
LGs.f2.6.0.5.sd 
```

Third, we get the genetic mapping of linkage groups

```{r}
set_map_fun(type="kosambi")

LG.f2.6.0.5.1.sd <- make_seq(LGs.f2.6.0.5.sd, 1)
LG.f2.6.0.5.2.sd <- make_seq(LGs.f2.6.0.5.sd, 2)
LG.f2.6.0.5.3.sd <- make_seq(LGs.f2.6.0.5.sd, 3)
LG.f2.6.0.5.4.sd <- make_seq(LGs.f2.6.0.5.sd, 4)
LG.f2.6.0.5.5.sd <- make_seq(LGs.f2.6.0.5.sd, 5)
LG.f2.6.0.5.6.sd <- make_seq(LGs.f2.6.0.5.sd, 6)
LG.f2.6.0.5.7.sd <- make_seq(LGs.f2.6.0.5.sd, 7)
LG.f2.6.0.5.8.sd <- make_seq(LGs.f2.6.0.5.sd, 8)
LG.f2.6.0.5.9.sd <- make_seq(LGs.f2.6.0.5.sd, 9)
LG.f2.6.0.5.10.sd <- make_seq(LGs.f2.6.0.5.sd, 10)
LG.f2.6.0.5.11.sd <- make_seq(LGs.f2.6.0.5.sd, 11)
LG.f2.6.0.5.12.sd <- make_seq(LGs.f2.6.0.5.sd, 12)
LG.f2.6.0.5.13.sd <- make_seq(LGs.f2.6.0.5.sd, 13)
LG.f2.6.0.5.14.sd <- make_seq(LGs.f2.6.0.5.sd, 14)
LG.f2.6.0.5.15.sd <- make_seq(LGs.f2.6.0.5.sd, 15)
LG.f2.6.0.5.16.sd <- make_seq(LGs.f2.6.0.5.sd, 16)
LG.f2.6.0.5.17.sd <- make_seq(LGs.f2.6.0.5.sd, 17)
LG.f2.6.0.5.18.sd <- make_seq(LGs.f2.6.0.5.sd, 18)
LG.f2.6.0.5.19.sd <- make_seq(LGs.f2.6.0.5.sd, 19)
LG.f2.6.0.5.20.sd <- make_seq(LGs.f2.6.0.5.sd, 20)
LG.f2.6.0.5.21.sd <- make_seq(LGs.f2.6.0.5.sd, 21)
LG.f2.6.0.5.22.sd <- make_seq(LGs.f2.6.0.5.sd, 22)
LG.f2.6.0.5.23.sd <- make_seq(LGs.f2.6.0.5.sd, 23)
LG.f2.6.0.5.24.sd <- make_seq(LGs.f2.6.0.5.sd, 24)
LG.f2.6.0.5.25.sd <- make_seq(LGs.f2.6.0.5.sd, 25)
LG.f2.6.0.5.26.sd <- make_seq(LGs.f2.6.0.5.sd, 26)
LG.f2.6.0.5.27.sd <- make_seq(LGs.f2.6.0.5.sd, 27)
LG.f2.6.0.5.28.sd <- make_seq(LGs.f2.6.0.5.sd, 28)
LG.f2.6.0.5.29.sd <- make_seq(LGs.f2.6.0.5.sd, 29)
LG.f2.6.0.5.30.sd <- make_seq(LGs.f2.6.0.5.sd, 30)
LG.f2.6.0.5.31.sd <- make_seq(LGs.f2.6.0.5.sd, 31)




LG.f2.6.0.5.1.ord.sd <- order_seq(LG.f2.6.0.5.1.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.2.ord.sd <- order_seq(LG.f2.6.0.5.2.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.3.ord.sd <- order_seq(LG.f2.6.0.5.3.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.4.ord.sd <- order_seq(LG.f2.6.0.5.4.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.5.ord.sd <- order_seq(LG.f2.6.0.5.5.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.6.ord.sd <- order_seq(LG.f2.6.0.5.6.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.7.ord.sd <- order_seq(LG.f2.6.0.5.7.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.8.ord.sd <- order_seq(LG.f2.6.0.5.8.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.9.ord.sd <- order_seq(LG.f2.6.0.5.9.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.10.ord.sd <- order_seq(LG.f2.6.0.5.10.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.11.ord.sd <- order_seq(LG.f2.6.0.5.11.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.12.ord.sd <- order_seq(LG.f2.6.0.5.12.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.13.ord.sd <- order_seq(LG.f2.6.0.5.13.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.14.ord.sd <- order_seq(LG.f2.6.0.5.14.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.15.ord.sd <- order_seq(LG.f2.6.0.5.15.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.16.ord.sd <- order_seq(LG.f2.6.0.5.16.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.17.ord.sd <- order_seq(LG.f2.6.0.5.17.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.18.ord.sd <- order_seq(LG.f2.6.0.5.18.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.19.ord.sd <- order_seq(LG.f2.6.0.5.19.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.20.ord.sd <- order_seq(LG.f2.6.0.5.20.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.21.ord.sd <- order_seq(LG.f2.6.0.5.21.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.22.ord.sd <- order_seq(LG.f2.6.0.5.22.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.23.ord.sd <- order_seq(LG.f2.6.0.5.23.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.24.ord.sd <- order_seq(LG.f2.6.0.5.24.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.25.ord.sd <- order_seq(LG.f2.6.0.5.25.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.26.ord.sd <- order_seq(LG.f2.6.0.5.26.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.27.ord.sd <- order_seq(LG.f2.6.0.5.27.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.28.ord.sd <- order_seq(LG.f2.6.0.5.28.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.29.ord.sd <- order_seq(LG.f2.6.0.5.29.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.30.ord.sd <- order_seq(LG.f2.6.0.5.30.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.31.ord.sd <- order_seq(LG.f2.6.0.5.31.sd, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)


```

Now, we order the markers, all of them and only the safe ones

```{r}
LG.f2.6.0.5.1.ord.safe.sd <- make_seq(LG.f2.6.0.5.1.ord.sd,"safe")
LG.f2.6.0.5.2.ord.safe.sd <- make_seq(LG.f2.6.0.5.2.ord.sd,"safe")
LG.f2.6.0.5.3.ord.safe.sd <- make_seq(LG.f2.6.0.5.3.ord.sd,"safe")
LG.f2.6.0.5.4.ord.safe.sd <- make_seq(LG.f2.6.0.5.4.ord.sd,"safe")
LG.f2.6.0.5.5.ord.safe.sd <- make_seq(LG.f2.6.0.5.5.ord.sd,"safe")
LG.f2.6.0.5.6.ord.safe.sd <- make_seq(LG.f2.6.0.5.6.ord.sd,"safe")
LG.f2.6.0.5.7.ord.safe.sd <- make_seq(LG.f2.6.0.5.7.ord.sd,"safe")
LG.f2.6.0.5.8.ord.safe.sd <- make_seq(LG.f2.6.0.5.8.ord.sd,"safe")
LG.f2.6.0.5.9.ord.safe.sd <- make_seq(LG.f2.6.0.5.9.ord.sd,"safe")
LG.f2.6.0.5.10.ord.safe.sd <- make_seq(LG.f2.6.0.5.10.ord.sd,"safe")
LG.f2.6.0.5.11.ord.safe.sd <- make_seq(LG.f2.6.0.5.11.ord.sd,"safe")
LG.f2.6.0.5.12.ord.safe.sd <- make_seq(LG.f2.6.0.5.12.ord.sd,"safe")
LG.f2.6.0.5.13.ord.safe.sd <- make_seq(LG.f2.6.0.5.13.ord.sd,"safe")
LG.f2.6.0.5.14.ord.safe.sd <- make_seq(LG.f2.6.0.5.14.ord.sd,"safe")
LG.f2.6.0.5.15.ord.safe.sd <- make_seq(LG.f2.6.0.5.15.ord.sd,"safe")
LG.f2.6.0.5.16.ord.safe.sd <- make_seq(LG.f2.6.0.5.16.ord.sd,"safe")
LG.f2.6.0.5.17.ord.safe.sd <- make_seq(LG.f2.6.0.5.17.ord.sd,"safe")
LG.f2.6.0.5.18.ord.safe.sd <- make_seq(LG.f2.6.0.5.18.ord.sd,"safe")
LG.f2.6.0.5.19.ord.safe.sd <- make_seq(LG.f2.6.0.5.19.ord.sd,"safe")
LG.f2.6.0.5.20.ord.safe.sd <- make_seq(LG.f2.6.0.5.20.ord.sd,"safe")
LG.f2.6.0.5.21.ord.safe.sd <- make_seq(LG.f2.6.0.5.21.ord.sd,"safe")
LG.f2.6.0.5.22.ord.safe.sd <- make_seq(LG.f2.6.0.5.22.ord.sd,"safe")
LG.f2.6.0.5.23.ord.safe.sd <- make_seq(LG.f2.6.0.5.23.ord.sd,"safe")
LG.f2.6.0.5.24.ord.safe.sd <- make_seq(LG.f2.6.0.5.24.ord.sd,"safe")
LG.f2.6.0.5.25.ord.safe.sd <- make_seq(LG.f2.6.0.5.25.ord.sd,"safe")
LG.f2.6.0.5.26.ord.safe.sd <- make_seq(LG.f2.6.0.5.26.ord.sd,"safe")
LG.f2.6.0.5.27.ord.safe.sd <- make_seq(LG.f2.6.0.5.27.ord.sd,"safe")
LG.f2.6.0.5.28.ord.safe.sd <- make_seq(LG.f2.6.0.5.28.ord.sd,"safe")
LG.f2.6.0.5.29.ord.safe.sd <- make_seq(LG.f2.6.0.5.29.ord.sd,"safe")
LG.f2.6.0.5.30.ord.safe.sd <- make_seq(LG.f2.6.0.5.30.ord.sd,"safe")
LG.f2.6.0.5.31.ord.safe.sd <- make_seq(LG.f2.6.0.5.31.ord.sd,"safe")

LG.f2.6.0.5.1.ord.all.sd <- make_seq(LG.f2.6.0.5.1.ord.sd,"force")
LG.f2.6.0.5.2.ord.all.sd <- make_seq(LG.f2.6.0.5.2.ord.sd,"force")
LG.f2.6.0.5.3.ord.all.sd <- make_seq(LG.f2.6.0.5.3.ord.sd,"force")
LG.f2.6.0.5.4.ord.all.sd <- make_seq(LG.f2.6.0.5.4.ord.sd,"force")
LG.f2.6.0.5.5.ord.all.sd <- make_seq(LG.f2.6.0.5.5.ord.sd,"force")
LG.f2.6.0.5.6.ord.all.sd <- make_seq(LG.f2.6.0.5.6.ord.sd,"force")
LG.f2.6.0.5.7.ord.all.sd <- make_seq(LG.f2.6.0.5.7.ord.sd,"force")
LG.f2.6.0.5.8.ord.all.sd <- make_seq(LG.f2.6.0.5.8.ord.sd,"force")
LG.f2.6.0.5.9.ord.all.sd <- make_seq(LG.f2.6.0.5.9.ord.sd,"force")
LG.f2.6.0.5.10.ord.all.sd <- make_seq(LG.f2.6.0.5.10.ord.sd,"force")
LG.f2.6.0.5.11.ord.all.sd <- make_seq(LG.f2.6.0.5.11.ord.sd,"force")
LG.f2.6.0.5.12.ord.all.sd <- make_seq(LG.f2.6.0.5.12.ord.sd,"force")
LG.f2.6.0.5.13.ord.all.sd <- make_seq(LG.f2.6.0.5.13.ord.sd,"force")
LG.f2.6.0.5.14.ord.all.sd <- make_seq(LG.f2.6.0.5.14.ord.sd,"force")
LG.f2.6.0.5.15.ord.all.sd <- make_seq(LG.f2.6.0.5.15.ord.sd,"force")
LG.f2.6.0.5.16.ord.all.sd <- make_seq(LG.f2.6.0.5.16.ord.sd,"force")
LG.f2.6.0.5.17.ord.all.sd <- make_seq(LG.f2.6.0.5.17.ord.sd,"force")
LG.f2.6.0.5.18.ord.all.sd <- make_seq(LG.f2.6.0.5.18.ord.sd,"force")
LG.f2.6.0.5.19.ord.all.sd <- make_seq(LG.f2.6.0.5.19.ord.sd,"force")
LG.f2.6.0.5.20.ord.all.sd <- make_seq(LG.f2.6.0.5.20.ord.sd,"force")
LG.f2.6.0.5.21.ord.all.sd <- make_seq(LG.f2.6.0.5.21.ord.sd,"force")
LG.f2.6.0.5.22.ord.all.sd <- make_seq(LG.f2.6.0.5.22.ord.sd,"force")
LG.f2.6.0.5.23.ord.all.sd <- make_seq(LG.f2.6.0.5.23.ord.sd,"force")
LG.f2.6.0.5.24.ord.all.sd <- make_seq(LG.f2.6.0.5.24.ord.sd,"force")
LG.f2.6.0.5.25.ord.all.sd <- make_seq(LG.f2.6.0.5.25.ord.sd,"force")
LG.f2.6.0.5.26.ord.all.sd <- make_seq(LG.f2.6.0.5.26.ord.sd,"force")
LG.f2.6.0.5.27.ord.all.sd <- make_seq(LG.f2.6.0.5.27.ord.sd,"force")
LG.f2.6.0.5.28.ord.all.sd <- make_seq(LG.f2.6.0.5.28.ord.sd,"force")
LG.f2.6.0.5.29.ord.all.sd <- make_seq(LG.f2.6.0.5.29.ord.sd,"force")
LG.f2.6.0.5.30.ord.all.sd <- make_seq(LG.f2.6.0.5.30.ord.sd,"force")
LG.f2.6.0.5.31.ord.all.sd <- make_seq(LG.f2.6.0.5.31.ord.sd,"force")

```

Drawing the genetic map

```{r}
Map.6.0.5.ord.safe.sd <- list(
LG.f2.6.0.5.1.ord.safe.sd, 
LG.f2.6.0.5.2.ord.safe.sd, 
LG.f2.6.0.5.3.ord.safe.sd, 
LG.f2.6.0.5.4.ord.safe.sd, 
LG.f2.6.0.5.5.ord.safe.sd, 
LG.f2.6.0.5.6.ord.safe.sd, 
LG.f2.6.0.5.7.ord.safe.sd, 
LG.f2.6.0.5.8.ord.safe.sd, 
LG.f2.6.0.5.9.ord.safe.sd, 
LG.f2.6.0.5.10.ord.safe.sd,
LG.f2.6.0.5.11.ord.safe.sd,
LG.f2.6.0.5.12.ord.safe.sd,
LG.f2.6.0.5.13.ord.safe.sd,
LG.f2.6.0.5.14.ord.safe.sd,
LG.f2.6.0.5.15.ord.safe.sd,
LG.f2.6.0.5.16.ord.safe.sd,
LG.f2.6.0.5.17.ord.safe.sd,
LG.f2.6.0.5.18.ord.safe.sd,
LG.f2.6.0.5.19.ord.safe.sd,
LG.f2.6.0.5.20.ord.safe.sd,
LG.f2.6.0.5.21.ord.safe.sd,
LG.f2.6.0.5.22.ord.safe.sd,
LG.f2.6.0.5.23.ord.safe.sd,
LG.f2.6.0.5.24.ord.safe.sd,
LG.f2.6.0.5.25.ord.safe.sd,
LG.f2.6.0.5.26.ord.safe.sd,
LG.f2.6.0.5.27.ord.safe.sd,
LG.f2.6.0.5.28.ord.safe.sd,
LG.f2.6.0.5.29.ord.safe.sd,
LG.f2.6.0.5.30.ord.safe.sd,
LG.f2.6.0.5.31.ord.safe.sd)

Map.6.0.5.ord.all.sd <- list(
LG.f2.6.0.5.1.ord.all.sd, 
LG.f2.6.0.5.2.ord.all.sd, 
LG.f2.6.0.5.3.ord.all.sd, 
LG.f2.6.0.5.4.ord.all.sd, 
LG.f2.6.0.5.5.ord.all.sd, 
LG.f2.6.0.5.6.ord.all.sd, 
LG.f2.6.0.5.7.ord.all.sd, 
LG.f2.6.0.5.8.ord.all.sd, 
LG.f2.6.0.5.9.ord.all.sd, 
LG.f2.6.0.5.10.ord.all.sd,
LG.f2.6.0.5.11.ord.all.sd,
LG.f2.6.0.5.12.ord.all.sd,
LG.f2.6.0.5.13.ord.all.sd,
LG.f2.6.0.5.14.ord.all.sd,
LG.f2.6.0.5.15.ord.all.sd,
LG.f2.6.0.5.16.ord.all.sd,
LG.f2.6.0.5.17.ord.all.sd,
LG.f2.6.0.5.18.ord.all.sd,
LG.f2.6.0.5.19.ord.all.sd,
LG.f2.6.0.5.20.ord.all.sd,
LG.f2.6.0.5.21.ord.all.sd,
LG.f2.6.0.5.22.ord.all.sd,
LG.f2.6.0.5.23.ord.all.sd,
LG.f2.6.0.5.24.ord.all.sd,
LG.f2.6.0.5.25.ord.all.sd,
LG.f2.6.0.5.26.ord.all.sd,
LG.f2.6.0.5.27.ord.all.sd,
LG.f2.6.0.5.28.ord.all.sd,
LG.f2.6.0.5.29.ord.all.sd,
LG.f2.6.0.5.30.ord.all.sd,
LG.f2.6.0.5.31.ord.all.sd)

pdf("Map.6.0.5.ord.safe.sd.pdf")
draw_map(Map.6.0.5.ord.safe.sd, names= TRUE, grid=TRUE, cex.mrk=0.3)
dev.off()

pdf("Map.6.0.5.ord.all.sd.pdf")
draw_map(Map.6.0.5.ord.all.sd, names= TRUE, grid=TRUE, cex.mrk=0.3)
dev.off()

```


NOTE: This map is suboptimal because we have include many loci (85) under severe segregation distorion. So we are not going to "clean" the LGs as we did with the previous map. 

Now we are going to look for linkage groups with a higher number than markers under segregation distortion that what would be expected by chance.
But first we will check wether or not there is a correlation between missing data and segregation distortion.

```{r}

mydata.sd <- read.csv(file="permutations2.csv")
mydata.sd
mydata.sd[,1] <- paste("M",mydata.sd[,1], sep="")

x2.sd <- mydata.sd[,2]
missingdata.sd <- mydata.sd[,3]
summary(lm(x2.sd ~ missingdata.sd))
plot(x2.sd ~ missingdata.sd, main="", xlab = "Number of individuals missing the marker", ylab = "Segregation distortion (X-square)")

mydata.sd[,4] <- seq(1:1427)

LG1.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.1.ord.all.sd$seq.num),]
LG1.sd
nrow(LG1.sd)
LG1.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG1.sd))
for (j in 1:1000) LG1.per.sd[j,] <- sample(x2.sd, nrow(LG1.sd), replace = FALSE, prob = NULL)
histLG1.sd <- vector()
for (i in 1:1000) histLG1.sd[i] <- length(LG1.per.sd[i,][LG1.per.sd[i,]>5.991])
hist(histLG1.sd)
abline(v=length(LG1.sd[,2][LG1.sd[,2]>5.991]),col="red")
length(LG1.sd[,2][LG1.sd[,2]>13.5])

LG2.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.2.ord.all.sd$seq.num),]
LG2.sd
nrow(LG2.sd)
LG2.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG2.sd))
for (j in 1:1000) LG2.per.sd[j,] <- sample(x2.sd, nrow(LG2.sd), replace = FALSE, prob = NULL)
histLG2.sd <- vector()
for (i in 1:1000) histLG2.sd[i] <- length(LG2.per.sd[i,][LG2.per.sd[i,]>5.991])
hist(histLG2.sd)
abline(v=length(LG2.sd[,2][LG2.sd[,2]>5.991]),col="red")
length(LG2.sd[,2][LG2.sd[,2]>13.5])

LG3.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.3.ord.all.sd$seq.num),]
LG3.sd
nrow(LG3.sd)
LG3.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG3.sd))
for (j in 1:1000) LG3.per.sd[j,] <- sample(x2.sd, nrow(LG3.sd), replace = FALSE, prob = NULL)
histLG3.sd <- vector()
for (i in 1:1000) histLG3.sd[i] <- length(LG3.per.sd[i,][LG3.per.sd[i,]>5.991])
hist(histLG3.sd)
abline(v=length(LG3.sd[,2][LG3.sd[,2]>5.991]),col="red")
length(LG3.sd[,2][LG3.sd[,2]>13.5])


LG4.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.4.ord.all.sd$seq.num),]
LG4.sd
nrow(LG4.sd)
LG4.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG4.sd))
for (j in 1:1000) LG4.per.sd[j,] <- sample(x2.sd, nrow(LG4.sd), replace = FALSE, prob = NULL)
histLG4.sd <- vector()
for (i in 1:1000) histLG4.sd[i] <- length(LG4.per.sd[i,][LG4.per.sd[i,]>5.991])
hist(histLG4.sd, xlim = c(0,60))
abline(v=length(LG4.sd[,2][LG4.sd[,2]>5.991]),col="red")
length(LG4.sd[,2][LG4.sd[,2]>13.5])

LG5.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.5.ord.all.sd$seq.num),]
LG5.sd
nrow(LG5.sd)
LG5.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG5.sd))
for (j in 1:1000) LG5.per.sd[j,] <- sample(x2.sd, nrow(LG5.sd), replace = FALSE, prob = NULL)
histLG5.sd <- vector()
for (i in 1:1000) histLG5.sd[i] <- length(LG5.per.sd[i,][LG5.per.sd[i,]>5.991])
hist(histLG5.sd)
abline(v=length(LG5.sd[,2][LG5.sd[,2]>5.991]),col="red")
length(LG5.sd[,2][LG5.sd[,2]>13.5])


LG6.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.6.ord.all.sd$seq.num),]
LG6.sd
nrow(LG6.sd)
LG6.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG6.sd))
for (j in 1:1000) LG6.per.sd[j,] <- sample(x2.sd, nrow(LG6.sd), replace = FALSE, prob = NULL)
histLG6.sd <- vector()
for (i in 1:1000) histLG6.sd[i] <- length(LG6.per.sd[i,][LG6.per.sd[i,]>5.991])
hist(histLG6.sd)
abline(v=length(LG6.sd[,2][LG6.sd[,2]>5.991]),col="red")
length(LG6.sd[,2][LG6.sd[,2]>13.5])


LG7.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.7.ord.all.sd$seq.num),]
LG7.sd
nrow(LG7.sd)
LG7.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG7.sd))
for (j in 1:1000) LG7.per.sd[j,] <- sample(x2.sd, nrow(LG7.sd), replace = FALSE, prob = NULL)
histLG7.sd <- vector()
for (i in 1:1000) histLG7.sd[i] <- length(LG7.per.sd[i,][LG7.per.sd[i,]>5.991])
hist(histLG7.sd)
abline(v=length(LG7.sd[,2][LG7.sd[,2]>5.991]),col="red")
length(LG7.sd[,2][LG7.sd[,2]>13.5])

LG8.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.8.ord.all.sd$seq.num),]
LG8.sd
nrow(LG8.sd)
LG8.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG8.sd))
for (j in 1:1000) LG8.per.sd[j,] <- sample(x2.sd, nrow(LG8.sd), replace = FALSE, prob = NULL)
histLG8.sd <- vector()
for (i in 1:1000) histLG8.sd[i] <- length(LG8.per.sd[i,][LG8.per.sd[i,]>5.991])
hist(histLG8.sd)
abline(v=length(LG8.sd[,2][LG8.sd[,2]>5.991]),col="red")
length(LG8.sd[,2][LG8.sd[,2]>13.5])

LG9.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.9.ord.all.sd$seq.num),]
LG9.sd
nrow(LG9.sd)
LG9.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG9.sd))
for (j in 1:1000) LG9.per.sd[j,] <- sample(x2.sd, nrow(LG9.sd), replace = FALSE, prob = NULL)
histLG9.sd <- vector()
for (i in 1:1000) histLG9.sd[i] <- length(LG9.per.sd[i,][LG9.per.sd[i,]>5.991])
hist(histLG9.sd, xlim = c(0,30))
abline(v=length(LG9.sd[,2][LG9.sd[,2]>5.991]),col="red")
length(LG9.sd[,2][LG9.sd[,2]>13.5])

LG10.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.10.ord.all.sd$seq.num),]
LG10.sd
nrow(LG10.sd)
LG10.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG10.sd))
for (j in 1:1000) LG10.per.sd[j,] <- sample(x2.sd, nrow(LG10.sd), replace = FALSE, prob = NULL)
histLG10.sd <- vector()
for (i in 1:1000) histLG10.sd[i] <- length(LG10.per.sd[i,][LG10.per.sd[i,]>5.991])
hist(histLG10.sd)
abline(v=length(LG10.sd[,2][LG10.sd[,2]>5.991]),col="red")
length(LG10.sd[,2][LG10.sd[,2]>13.5])

LG11.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.11.ord.all.sd$seq.num),]
LG11.sd
nrow(LG11.sd)
LG11.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG11.sd))
for (j in 1:1000) LG11.per.sd[j,] <- sample(x2.sd, nrow(LG11.sd), replace = FALSE, prob = NULL)
histLG11.sd <- vector()
for (i in 1:1000) histLG11.sd[i] <- length(LG11.per.sd[i,][LG11.per.sd[i,]>5.991])
hist(histLG11.sd)
abline(v=length(LG11.sd[,2][LG11.sd[,2]>5.991]),col="red")
length(LG11.sd[,2][LG11.sd[,2]>13.5])

LG12.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.12.ord.all.sd$seq.num),]
LG12.sd
nrow(LG12.sd)
LG12.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG12.sd))
for (j in 1:1000) LG12.per.sd[j,] <- sample(x2.sd, nrow(LG12.sd), replace = FALSE, prob = NULL)
histLG12.sd <- vector()
for (i in 1:1000) histLG12.sd[i] <- length(LG12.per.sd[i,][LG12.per.sd[i,]>5.991])
hist(histLG12.sd)
abline(v=length(LG12.sd[,2][LG12.sd[,2]>5.991]),col="red")
length(LG12.sd[,2][LG12.sd[,2]>13.5])

LG13.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.13.ord.all.sd$seq.num),]
LG13.sd
nrow(LG13.sd)
LG13.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG13.sd))
for (j in 1:1000) LG13.per.sd[j,] <- sample(x2.sd, nrow(LG13.sd), replace = FALSE, prob = NULL)
histLG13.sd <- vector()
for (i in 1:1000) histLG13.sd[i] <- length(LG13.per.sd[i,][LG13.per.sd[i,]>5.991])
hist(histLG13.sd, xlim = c(2,21))
abline(v=length(LG13.sd[,2][LG13.sd[,2]>5.991]),col="red")
length(LG13.sd[,2][LG13.sd[,2]>13.5])

LG14.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.14.ord.all.sd$seq.num),]
LG14.sd
nrow(LG14.sd)
LG14.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG14.sd))
for (j in 1:1000) LG14.per.sd[j,] <- sample(x2.sd, nrow(LG14.sd), replace = FALSE, prob = NULL)
histLG14.sd <- vector()
for (i in 1:1000) histLG14.sd[i] <- length(LG14.per.sd[i,][LG14.per.sd[i,]>5.991])
hist(histLG14.sd)
abline(v=length(LG14.sd[,2][LG14.sd[,2]>5.991]),col="red")
length(LG14.sd[,2][LG14.sd[,2]>13.5])

LG15.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.15.ord.all.sd$seq.num),]
LG15.sd
nrow(LG15.sd)
LG15.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG15.sd))
for (j in 1:1000) LG15.per.sd[j,] <- sample(x2.sd, nrow(LG15.sd), replace = FALSE, prob = NULL)
histLG15.sd <- vector()
for (i in 1:1000) histLG15.sd[i] <- length(LG15.per.sd[i,][LG15.per.sd[i,]>5.991])
hist(histLG15.sd)
abline(v=length(LG15.sd[,2][LG15.sd[,2]>5.991]),col="red")
length(LG15.sd[,2][LG15.sd[,2]>13.5])

LG16.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.16.ord.all.sd$seq.num),]
LG16.sd
nrow(LG16.sd)
LG16.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG16.sd))
for (j in 1:1000) LG16.per.sd[j,] <- sample(x2.sd, nrow(LG16.sd), replace = FALSE, prob = NULL)
histLG16.sd <- vector()
for (i in 1:1000) histLG16.sd[i] <- length(LG16.per.sd[i,][LG16.per.sd[i,]>5.991])
hist(histLG16.sd)
abline(v=length(LG16.sd[,2][LG16.sd[,2]>5.991]),col="red")
length(LG16.sd[,2][LG16.sd[,2]>13.5])

LG17.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.17.ord.all.sd$seq.num),]
LG17.sd
nrow(LG17.sd)
LG17.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG17.sd))
for (j in 1:1000) LG17.per.sd[j,] <- sample(x2.sd, nrow(LG17.sd), replace = FALSE, prob = NULL)
histLG17.sd <- vector()
for (i in 1:1000) histLG17.sd[i] <- length(LG17.per.sd[i,][LG17.per.sd[i,]>5.991])
hist(histLG17.sd, xlim = c(5,50))
abline(v=length(LG17.sd[,2][LG17.sd[,2]>5.991]),col="red")
length(LG17.sd[,2][LG17.sd[,2]>13.5])

LG18.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.18.ord.all.sd$seq.num),]
LG18.sd
nrow(LG18.sd)
LG18.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG18.sd))
for (j in 1:1000) LG18.per.sd[j,] <- sample(x2.sd, nrow(LG18.sd), replace = FALSE, prob = NULL)
histLG18.sd <- vector()
for (i in 1:1000) histLG18.sd[i] <- length(LG18.per.sd[i,][LG18.per.sd[i,]>5.991])
hist(histLG18.sd)
abline(v=length(LG18.sd[,2][LG18.sd[,2]>5.991]),col="red")
length(LG18.sd[,2][LG18.sd[,2]>13.5])

LG19.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.19.ord.all.sd$seq.num),]
LG19.sd
nrow(LG19.sd)
LG19.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG19.sd))
for (j in 1:1000) LG19.per.sd[j,] <- sample(x2.sd, nrow(LG19.sd), replace = FALSE, prob = NULL)
histLG19.sd <- vector()
for (i in 1:1000) histLG19.sd[i] <- length(LG19.per.sd[i,][LG19.per.sd[i,]>5.991])
hist(histLG19.sd)
abline(v=length(LG19.sd[,2][LG19.sd[,2]>5.991]),col="red")
length(LG19.sd[,2][LG19.sd[,2]>13.5])

LG20.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.20.ord.all.sd$seq.num),]
LG20.sd
nrow(LG20.sd)
LG20.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG20.sd))
for (j in 1:1000) LG20.per.sd[j,] <- sample(x2.sd, nrow(LG20.sd), replace = FALSE, prob = NULL)
histLG20.sd <- vector()
for (i in 1:1000) histLG20.sd[i] <- length(LG20.per.sd[i,][LG20.per.sd[i,]>5.991])
hist(histLG20.sd)
abline(v=length(LG20.sd[,2][LG20.sd[,2]>5.991]),col="red")
length(LG20.sd[,2][LG20.sd[,2]>13.5])

LG21.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.21.ord.all.sd$seq.num),]
LG21.sd
nrow(LG21.sd)
LG21.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG21.sd))
for (j in 1:1000) LG21.per.sd[j,] <- sample(x2.sd, nrow(LG21.sd), replace = FALSE, prob = NULL)
histLG21.sd <- vector()
for (i in 1:1000) histLG21.sd[i] <- length(LG21.per.sd[i,][LG21.per.sd[i,]>5.991])
hist(histLG21.sd)
abline(v=length(LG21.sd[,2][LG21.sd[,2]>5.991]),col="red")
length(LG21.sd[,2][LG21.sd[,2]>13.5])

LG22.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.22.ord.all.sd$seq.num),]
LG22.sd
nrow(LG22.sd)
LG22.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG22.sd))
for (j in 1:1000) LG22.per.sd[j,] <- sample(x2.sd, nrow(LG22.sd), replace = FALSE, prob = NULL)
histLG22.sd <- vector()
for (i in 1:1000) histLG22.sd[i] <- length(LG22.per.sd[i,][LG22.per.sd[i,]>5.991])
hist(histLG22.sd)
abline(v=length(LG22.sd[,2][LG22.sd[,2]>5.991]),col="red")
length(LG22.sd[,2][LG22.sd[,2]>13.5])

LG23.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.23.ord.all.sd$seq.num),]
LG23.sd
nrow(LG23.sd)
LG23.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG23.sd))
for (j in 1:1000) LG23.per.sd[j,] <- sample(x2.sd, nrow(LG23.sd), replace = FALSE, prob = NULL)
histLG23.sd <- vector()
for (i in 1:1000) histLG23.sd[i] <- length(LG23.per.sd[i,][LG23.per.sd[i,]>5.991])
hist(histLG23.sd, xlim=c(0,13))
abline(v=length(LG23.sd[,2][LG23.sd[,2]>5.991]),col="red")
length(LG23.sd[,2][LG23.sd[,2]>13.5])

LG24.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.24.ord.all.sd$seq.num),]
LG24.sd
nrow(LG24.sd)
LG24.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG24.sd))
for (j in 1:1000) LG24.per.sd[j,] <- sample(x2.sd, nrow(LG24.sd), replace = FALSE, prob = NULL)
histLG24.sd <- vector()
for (i in 1:1000) histLG24.sd[i] <- length(LG24.per.sd[i,][LG24.per.sd[i,]>5.991])
hist(histLG24.sd)
abline(v=length(LG24.sd[,2][LG24.sd[,2]>5.991]),col="red")
length(LG24.sd[,2][LG24.sd[,2]>13.5])

LG25.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.25.ord.all.sd$seq.num),]
LG25.sd
nrow(LG25.sd)
LG25.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG25.sd))
for (j in 1:1000) LG25.per.sd[j,] <- sample(x2.sd, nrow(LG25.sd), replace = FALSE, prob = NULL)
histLG25.sd <- vector()
for (i in 1:1000) histLG25.sd[i] <- length(LG25.per.sd[i,][LG25.per.sd[i,]>5.991])
hist(histLG25.sd)
abline(v=length(LG25.sd[,2][LG25.sd[,2]>5.991]),col="red")
length(LG25.sd[,2][LG25.sd[,2]>13.5])

LG26.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.26.ord.all.sd$seq.num),]
LG26.sd
nrow(LG26.sd)
LG26.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG26.sd))
for (j in 1:1000) LG26.per.sd[j,] <- sample(x2.sd, nrow(LG26.sd), replace = FALSE, prob = NULL)
histLG26.sd <- vector()
for (i in 1:1000) histLG26.sd[i] <- length(LG26.per.sd[i,][LG26.per.sd[i,]>5.991])
hist(histLG26.sd)
abline(v=length(LG26.sd[,2][LG26.sd[,2]>5.991]),col="red")
length(LG26.sd[,2][LG26.sd[,2]>13.5])

LG27.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.27.ord.all.sd$seq.num),]
LG27.sd
nrow(LG27.sd)
LG27.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG27.sd))
for (j in 1:1000) LG27.per.sd[j,] <- sample(x2.sd, nrow(LG27.sd), replace = FALSE, prob = NULL)
histLG27.sd <- vector()
for (i in 1:1000) histLG27.sd[i] <- length(LG27.per.sd[i,][LG27.per.sd[i,]>5.991])
hist(histLG27.sd)
abline(v=length(LG27.sd[,2][LG27.sd[,2]>5.991]),col="red")
length(LG27.sd[,2][LG27.sd[,2]>13.5])

LG28.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.28.ord.all.sd$seq.num),]
LG28.sd
nrow(LG28.sd)
LG28.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG28.sd))
for (j in 1:1000) LG28.per.sd[j,] <- sample(x2.sd, nrow(LG28.sd), replace = FALSE, prob = NULL)
histLG28.sd <- vector()
for (i in 1:1000) histLG28.sd[i] <- length(LG28.per.sd[i,][LG28.per.sd[i,]>5.991])
hist(histLG28.sd)
abline(v=length(LG28.sd[,2][LG28.sd[,2]>5.991]),col="red")
length(LG28.sd[,2][LG28.sd[,2]>13.5])

LG29.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.29.ord.all.sd$seq.num),]
LG29.sd
nrow(LG29.sd)
LG29.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG29.sd))
for (j in 1:1000) LG29.per.sd[j,] <- sample(x2.sd, nrow(LG29.sd), replace = FALSE, prob = NULL)
histLG29.sd <- vector()
for (i in 1:1000) histLG29.sd[i] <- length(LG29.per.sd[i,][LG29.per.sd[i,]>5.991])
hist(histLG29.sd)
abline(v=length(LG29.sd[,2][LG29.sd[,2]>5.991]),col="red")
length(LG29.sd[,2][LG29.sd[,2]>13.5])

LG30.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.30.ord.all.sd$seq.num),]
LG30.sd
nrow(LG30.sd)
LG30.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG30.sd))
for (j in 1:1000) LG30.per.sd[j,] <- sample(x2.sd, nrow(LG30.sd), replace = FALSE, prob = NULL)
histLG30.sd <- vector()
for (i in 1:1000) histLG30.sd[i] <- length(LG30.per.sd[i,][LG30.per.sd[i,]>5.991])
hist(histLG30.sd)
abline(v=length(LG30.sd[,2][LG30.sd[,2]>5.991]),col="red")
length(LG30.sd[,2][LG30.sd[,2]>13.5])

LG31.sd <- mydata.sd[intersect(mydata.sd[,4],LG.f2.6.0.5.31.ord.all.sd$seq.num),]
LG31.sd
nrow(LG31.sd)
LG31.per.sd <- matrix(0, nrow=1000, ncol = nrow(LG31.sd))
for (j in 1:1000) LG31.per.sd[j,] <- sample(x2.sd, nrow(LG31.sd), replace = FALSE, prob = NULL)
histLG31.sd <- vector()
for (i in 1:1000) histLG31.sd[i] <- length(LG31.per.sd[i,][LG31.per.sd[i,]>5.991])
hist(histLG31.sd)
abline(v=length(LG31.sd[,2][LG31.sd[,2]>5.991]),col="red")
length(LG31.sd[,2][LG31.sd[,2]>13.5])


```

Linkage groups 13, 17 and 31 (4 in this map) have more markers under segregation distortion that expected by chance

Now we are going to check whether or not those markers under segregation distortion are grouped together within the linkage groups.

And first, we will check again whether or not for these specific linkage groups there is any king of correlation between missing data and segregation distortion.

```{r}

x2 <- LG4.sd[,2]
missingdata <- LG4.sd[,3]
summary(lm(x2 ~ missingdata))
plot(x2 ~ missingdata, main="", xlab = "Number of individuals missing the marker", ylab = "Segregation distortion (X-square)")

x2 <- LG17.sd[,2]
missingdata <- LG17.sd[,3]
summary(lm(x2 ~ missingdata))
plot(x2 ~ missingdata, main="", xlab = "Number of individuals missing the marker", ylab = "Segregation distortion (X-square)")

x2 <- LG13.sd[,2]
missingdata <- LG13.sd[,3]
summary(lm(x2 ~ missingdata))
plot(x2 ~ missingdata, main="", xlab = "Number of individuals missing the marker", ylab = "Segregation distortion (X-square)")

LG13.pos.sd <- read.csv("LG13.sd.csv")
setdiff(LG13.pos.sd[,1],LG13.sd[,4])
setdiff(LG13.pos.sd[,2],LG13.sd[,1])

library(ggplot2)
LG13.pos.sd[,4] <- LG13.sd[,2][match(LG13.pos.sd[,2],LG13.sd[,1])]
names(LG13.pos.sd)[4] <- "CHISQUARE"
p13.sd <- ggplot(LG13.pos.sd, aes(POSITION))+
  geom_line(data=subset(LG13.pos.sd),aes(y=CHISQUARE),col="black", linetype="dotted")+
  geom_point(data=subset(LG13.pos.sd),aes(y=CHISQUARE),col="black")+
  scale_y_continuous(limits = c(0, 20))+
  geom_ribbon(data=subset(LG13.pos.sd),aes(ymin=0,ymax=5.991),alpha=0.5,fill="grey")+
  geom_errorbar(data=subset(LG13.pos.sd),aes(ymin=CHISQUARE,ymax=CHISQUARE),width=1)+
  theme_bw(base_size=20)+
  xlab('Distance (CentiMorgan)') +
  ylab('SD (CHISQUARE)')
p13.sd

LG4.pos.sd <- read.csv("LG4.sd.csv")
setdiff(LG4.pos.sd[,1],LG4.sd[,4])
setdiff(LG4.pos.sd[,2],LG4.sd[,1])

LG4.pos.sd[,4] <- LG4.sd[,2][match(LG4.pos.sd[,2],LG4.sd[,1])]
names(LG4.pos.sd)[4] <- "CHISQUARE"
p4.sd <- ggplot(LG4.pos.sd, aes(POSITION))+
  geom_line(data=subset(LG4.pos.sd),aes(y=CHISQUARE),col="black", linetype="dotted")+
  geom_point(data=subset(LG4.pos.sd),aes(y=CHISQUARE),col="black")+
  scale_y_continuous(limits = c(0, 60))+
  geom_ribbon(data=subset(LG4.pos.sd),aes(ymin=0,ymax=5.991),alpha=0.5,fill="grey")+
  geom_errorbar(data=subset(LG4.pos.sd),aes(ymin=CHISQUARE,ymax=CHISQUARE),width=1)+
  theme_bw(base_size=20)+
  xlab('Distance (CentiMorgan)') +
  ylab('SD (CHISQUARE)')
p4.sd


LG17.pos.sd <- read.csv("LG17.sd.csv")
setdiff(LG17.pos.sd[,1],LG17.sd[,4])
setdiff(LG17.pos.sd[,2],LG17.sd[,1])

LG17.pos.sd[,4] <- LG17.sd[,2][match(LG17.pos.sd[,2],LG17.sd[,1])]
names(LG17.pos.sd)[4] <- "CHISQUARE"
p17.sd <- ggplot(LG17.pos.sd, aes(POSITION))+
  geom_line(data=subset(LG17.pos.sd),aes(y=CHISQUARE),col="black", linetype="dotted")+
  geom_point(data=subset(LG17.pos.sd),aes(y=CHISQUARE),col="black")+
  scale_y_continuous(limits = c(0, 13.5))+
  geom_ribbon(data=subset(LG17.pos.sd),aes(ymin=0,ymax=5.991),alpha=0.5,fill="grey")+
  geom_errorbar(data=subset(LG17.pos.sd),aes(ymin=CHISQUARE,ymax=CHISQUARE),width=1)+
  theme_bw(base_size=20)+
  xlab('Distance (CentiMorgan)') +
  ylab('SD (CHISQUARE)')
p17.sd

library(adehabitat)
wawotest(as.numeric(LG4.sd$CHISQUARE > 5.991))
wawotest(as.numeric(LG17.sd$CHISQUARE > 5.991))
wawotest(as.numeric(LG13.sd$CHISQUARE > 5.991))

mydata.sd.2 <- read.csv("mydata.sd.2.csv")
LG4.sd.2 <- mydata.sd.2[intersect(mydata.sd.2[,1],LG.f2.6.0.5.4.ord.all.sd$seq.num),]
LG4.sd.2
mean(LG4.sd.2$ABPER)
sd(LG4.sd.2$ABPER)
mean(LG4.sd.2$APER)
sd(LG4.sd.2$APER)
mean(LG4.sd.2$BPER)
sd(LG4.sd.2$BPER)

LG13.sd.2 <- mydata.sd.2[intersect(mydata.sd.2[,1],LG.f2.6.0.5.13.ord.all.sd$seq.num),]
LG13.sd.2
mean(LG13.sd.2$ABPER)
sd(LG13.sd.2$ABPER)
mean(LG13.sd.2$APER)
sd(LG13.sd.2$APER)
mean(LG13.sd.2$BPER)
sd(LG13.sd.2$BPER)

LG17.sd.2 <- mydata.sd.2[intersect(mydata.sd.2[,1],LG.f2.6.0.5.17.ord.all.sd$seq.num),]
LG17.sd.2
mean(LG17.sd.2$ABPER)
sd(LG17.sd.2$ABPER)
mean(LG17.sd.2$APER)
sd(LG17.sd.2$APER)
mean(LG17.sd.2$BPER)
sd(LG17.sd.2$BPER)

```



#########################################################
AFTER SECOND REVIEW
########################################################
We are going to repeat the process but including the 85 loci under severe segregation distortion AFTER MAKING THE LINKAGE MAP

First, we load the package onemap and import the data set

```{r}

library (onemap)

f2.onemap.sd <- read_mapmaker(file = "onemap.f2.sd.txt")

```

Second, we assign markers to linkage groups

```{r}
twopts.sd <- rf_2pts(f2.onemap.sd, LOD=3, max.rf=0.5)
assigner <- cbind(seq(1:1427),colnames(f2.onemap.sd$geno))
markerswithhghsd <- setdiff(colnames(f2.onemap.sd$geno),colnames(f2.onemap$geno))
markerswithighsd2 <- assigner[assigner[,2] %in% markerswithhghsd, 1]
markerswithouthighsd <- setdiff(seq(1:1427), markerswithighsd2)

mark.all.sd2 <- make_seq(twopts.sd, markerswithouthighsd)
LGs.f2.6.0.5.sd2 <- group(mark.all.sd2, LOD = 6, max.rf = 0.5)
LGs.f2.6.0.5.sd2 
```

Third, we get the genetic mapping of linkage groups

```{r}

setdiff(colnames(f2.onemap.sd$geno)[LG.f2.6.0.5.1.sd$seq.num],colnames(f2.onemap$geno.mmk$geno)[LG.f2.6.0.5.1$seq.num]) 
setdiff(colnames(f2.onemap.sd$geno)[LG.f2.6.0.5.2.sd$seq.num],colnames(f2.onemap$geno.mmk$geno)[LG.f2.6.0.5.2$seq.num]) 
setdiff(colnames(f2.onemap.sd$geno)[LG.f2.6.0.5.3.sd$seq.num],colnames(f2.onemap$geno.mmk$geno)[LG.f2.6.0.5.3$seq.num]) 
setdiff(colnames(f2.onemap.sd$geno)[LG.f2.6.0.5.5.sd$seq.num],colnames(f2.onemap$geno.mmk$geno)[LG.f2.6.0.5.4$seq.num]) 
setdiff(colnames(f2.onemap.sd$geno)[LG.f2.6.0.5.6.sd$seq.num],colnames(f2.onemap$geno.mmk$geno)[LG.f2.6.0.5.5$seq.num]) 
setdiff(colnames(f2.onemap.sd$geno)[LG.f2.6.0.5.2.sd$seq.num],colnames(f2.onemap$geno.mmk$geno)[LG.f2.6.0.5.6$seq.num]) 

setdiff(colnames(f2.onemap.sd$geno)[LG.f2.6.0.5.2.sd$seq.num],rbind(colnames(f2.onemap$geno.mmk$geno)[LG.f2.6.0.5.6$seq.num],colnames(f2.onemap$geno.mmk$geno)[LG.f2.6.0.5.2$seq.num])) 

setdiff(colnames(f2.onemap.sd$geno)[LG.f2.6.0.5.7.sd$seq.num],colnames(f2.onemap$geno.mmk$geno)[LG.f2.6.0.5.7$seq.num]) 


set_map_fun(type="kosambi")

LG.f2.6.0.5.1.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 1)
LG1.sd[LG1.sd[,2]>13.5,] #no hsd markers

LG.f2.6.0.5.2.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 2)
LG2.sd[LG2.sd[,2]>13.5,]
#151   M4741 61.30508       7  151 B1 LG2
#420  M13558 40.21591       8  420 B2 LG6
#916  M29986 14.72571       9  916 B3 LG2
#1145 M36782 14.59091       8 1145 B3 LG2
#1205 M38604 15.01282      28 1205 B3 LG2
#1353 M43468 14.89286      16 1353 B3 LG2
#1422 M45603 26.58170      31 1422 B3 LG2
LG.f2.6.0.5.2.sd2 <- add_marker(LG.f2.6.0.5.2.sd2, c(151,916,1145,1205,1353,1422))

LG.f2.6.0.5.3.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 3)
LG3.sd[LG3.sd[,2]>13.5,]
LG.f2.6.0.5.3.sd2 <- add_marker(LG.f2.6.0.5.3.sd2, c(168,652,1122))

LG.f2.6.0.5.4.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 4)
LG5.sd[LG5.sd[,2]>13.5,]
LG.f2.6.0.5.4.sd2 <- add_marker(LG.f2.6.0.5.4.sd2, 393)

LG.f2.6.0.5.5.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 5)
LG6.sd[LG6.sd[,2]>13.5,] #no hsd markers

LG.f2.6.0.5.6.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 6)
LG2.sd[LG2.sd[,2]>13.5,]
#151   M4741 61.30508       7  151 B1 LG2
#420  M13558 40.21591       8  420 B2 LG6
#916  M29986 14.72571       9  916 B3 LG2
#1145 M36782 14.59091       8 1145 B3 LG2
#1205 M38604 15.01282      28 1205 B3 LG2
#1353 M43468 14.89286      16 1353 B3 LG2
#1422 M45603 26.58170      31 1422 B3 LG2
LG.f2.6.0.5.6.sd2 <- add_marker(LG.f2.6.0.5.6.sd2, 420)

LG.f2.6.0.5.7.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 7)
LG7.sd[LG7.sd[,2]>13.5,] #no hsd markers

LG.f2.6.0.5.8.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 8)
LG8.sd[LG8.sd[,2]>13.5,] #no hsd markers

LG.f2.6.0.5.9.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 9)
LG9.sd[LG9.sd[,2]>13.5,] #no hsd markers

LG.f2.6.0.5.10.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 10)
LG10.sd[LG10.sd[,2]>13.5,] #no hsd markers

LG.f2.6.0.5.11.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 11)
LG11.sd[LG11.sd[,2]>13.5,] #no hsd markers

LG.f2.6.0.5.12.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 12)
LG12.sd[LG12.sd[,2]>13.5,] #no hsd markers

LG.f2.6.0.5.13.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 13)
LG13.sd[LG13.sd[,2]>13.5,]
LG.f2.6.0.5.13.sd2 <- add_marker(LG.f2.6.0.5.13.sd2, c(165,1017,1183))

LG.f2.6.0.5.14.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 14)
LG14.sd[LG14.sd[,2]>13.5,] 
LG.f2.6.0.5.14.sd2 <- add_marker(LG.f2.6.0.5.14.sd2, c(757,948,1084))

LG.f2.6.0.5.15.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 15)
LG15.sd[LG15.sd[,2]>13.5,] #no hsd markers

LG.f2.6.0.5.16.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 16)
LG16.sd[LG16.sd[,2]>13.5,]
LG.f2.6.0.5.16.sd2 <- add_marker(LG.f2.6.0.5.16.sd2, c(457,1414))

LG.f2.6.0.5.17.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 17)
LG17.sd[LG17.sd[,2]>13.5,]
LG.f2.6.0.5.17.sd2 <- add_marker(LG.f2.6.0.5.17.sd2, 399)

LG.f2.6.0.5.18.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 18)
LG18.sd[LG18.sd[,2]>13.5,] #no hsd markers

LG.f2.6.0.5.19.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 19)
LG19.sd[LG19.sd[,2]>13.5,]
LG.f2.6.0.5.19.sd2 <- add_marker(LG.f2.6.0.5.19.sd2, 349)

LG.f2.6.0.5.20.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 20)
LG20.sd[LG20.sd[,2]>13.5,] #no hsd markers

LG.f2.6.0.5.21.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 21)
LG21.sd[LG21.sd[,2]>13.5,]
LG.f2.6.0.5.21.sd2 <- add_marker(LG.f2.6.0.5.21.sd2, c(50,200,414))

LG.f2.6.0.5.22.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 22)
LG22.sd[LG22.sd[,2]>13.5,]
LG.f2.6.0.5.22.sd2 <- add_marker(LG.f2.6.0.5.22.sd2, c(1129,1148))

LG.f2.6.0.5.23.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 23)
LG23.sd[LG23.sd[,2]>13.5,] #no hsd markers

LG.f2.6.0.5.24.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 24)
LG24.sd[LG24.sd[,2]>13.5,] #no hsd markers

LG.f2.6.0.5.25.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 25)
LG25.sd[LG25.sd[,2]>13.5,] 
LG.f2.6.0.5.25.sd2 <- add_marker(LG.f2.6.0.5.25.sd2, c(378,635))

LG.f2.6.0.5.26.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 26)
LG26.sd[LG26.sd[,2]>13.5,] #no hsd markers

LG.f2.6.0.5.27.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 27)
LG27.sd[LG27.sd[,2]>13.5,] 
LG.f2.6.0.5.27.sd2 <- add_marker(LG.f2.6.0.5.27.sd2, c(646,651,1114))

LG.f2.6.0.5.28.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 28)
LG28.sd[LG28.sd[,2]>13.5,] 
LG.f2.6.0.5.28.sd2 <- add_marker(LG.f2.6.0.5.28.sd2, 926)

LG.f2.6.0.5.29.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 29)
LG29.sd[LG29.sd[,2]>13.5,] #no hsd markers

LG.f2.6.0.5.30.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 30)
LG30.sd[LG30.sd[,2]>13.5,] #no hsd markers

LG.f2.6.0.5.31.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 31)
LG4.sd[LG4.sd[,2]>13.5,4]
LG.f2.6.0.5.31.sd2 <- add_marker(LG.f2.6.0.5.31.sd2, LG4.sd[LG4.sd[,2]>13.5,4])

LG.f2.6.0.5.32.sd2 <- make_seq(LGs.f2.6.0.5.sd2, 32)
LG31.sd[LG31.sd[,2]>13.5,] #no hsd markers



LG.f2.6.0.5.1.ord.sd2 <- order_seq(LG.f2.6.0.5.1.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.2.ord.sd2 <- order_seq(LG.f2.6.0.5.2.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.3.ord.sd2 <- order_seq(LG.f2.6.0.5.3.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.4.ord.sd2 <- order_seq(LG.f2.6.0.5.4.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.5.ord.sd2 <- order_seq(LG.f2.6.0.5.5.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.6.ord.sd2 <- order_seq(LG.f2.6.0.5.6.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.7.ord.sd2 <- order_seq(LG.f2.6.0.5.7.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.8.ord.sd2 <- order_seq(LG.f2.6.0.5.8.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.9.ord.sd2 <- order_seq(LG.f2.6.0.5.9.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.10.ord.sd2 <- order_seq(LG.f2.6.0.5.10.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.11.ord.sd2 <- order_seq(LG.f2.6.0.5.11.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.12.ord.sd2 <- order_seq(LG.f2.6.0.5.12.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.13.ord.sd2 <- order_seq(LG.f2.6.0.5.13.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.14.ord.sd2 <- order_seq(LG.f2.6.0.5.14.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.15.ord.sd2 <- order_seq(LG.f2.6.0.5.15.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.16.ord.sd2 <- order_seq(LG.f2.6.0.5.16.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.17.ord.sd2 <- order_seq(LG.f2.6.0.5.17.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.18.ord.sd2 <- order_seq(LG.f2.6.0.5.18.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.19.ord.sd2 <- order_seq(LG.f2.6.0.5.19.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.20.ord.sd2 <- order_seq(LG.f2.6.0.5.20.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.21.ord.sd2 <- order_seq(LG.f2.6.0.5.21.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.22.ord.sd2 <- order_seq(LG.f2.6.0.5.22.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.23.ord.sd2 <- order_seq(LG.f2.6.0.5.23.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.24.ord.sd2 <- order_seq(LG.f2.6.0.5.24.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.25.ord.sd2 <- order_seq(LG.f2.6.0.5.25.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.26.ord.sd2 <- order_seq(LG.f2.6.0.5.26.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.27.ord.sd2 <- order_seq(LG.f2.6.0.5.27.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.28.ord.sd2 <- order_seq(LG.f2.6.0.5.28.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.29.ord.sd2 <- order_seq(LG.f2.6.0.5.29.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.30.ord.sd2 <- order_seq(LG.f2.6.0.5.30.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.31.ord.sd2 <- order_seq(LG.f2.6.0.5.31.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)
LG.f2.6.0.5.32.ord.sd2 <- order_seq(LG.f2.6.0.5.32.sd2, n.init=5, subset.search = "twopt", twopt.alg = "rcd", THRES = 3)


```

Now, we order the markers, all of them and only the safe ones

```{r}
LG.f2.6.0.5.1.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.1.ord.sd2,"safe")
LG.f2.6.0.5.2.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.2.ord.sd2,"safe")
LG.f2.6.0.5.3.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.3.ord.sd2,"safe")
LG.f2.6.0.5.4.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.4.ord.sd2,"safe")
LG.f2.6.0.5.5.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.5.ord.sd2,"safe")
LG.f2.6.0.5.6.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.6.ord.sd2,"safe")
LG.f2.6.0.5.7.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.7.ord.sd2,"safe")
LG.f2.6.0.5.8.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.8.ord.sd2,"safe")
LG.f2.6.0.5.9.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.9.ord.sd2,"safe")
LG.f2.6.0.5.10.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.10.ord.sd2,"safe")
LG.f2.6.0.5.11.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.11.ord.sd2,"safe")
LG.f2.6.0.5.12.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.12.ord.sd2,"safe")
LG.f2.6.0.5.13.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.13.ord.sd2,"safe")
LG.f2.6.0.5.14.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.14.ord.sd2,"safe")
LG.f2.6.0.5.15.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.15.ord.sd2,"safe")
LG.f2.6.0.5.16.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.16.ord.sd2,"safe")
LG.f2.6.0.5.17.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.17.ord.sd2,"safe")
LG.f2.6.0.5.18.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.18.ord.sd2,"safe")
LG.f2.6.0.5.19.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.19.ord.sd2,"safe")
LG.f2.6.0.5.20.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.20.ord.sd2,"safe")
LG.f2.6.0.5.21.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.21.ord.sd2,"safe")
LG.f2.6.0.5.22.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.22.ord.sd2,"safe")
LG.f2.6.0.5.23.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.23.ord.sd2,"safe")
LG.f2.6.0.5.24.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.24.ord.sd2,"safe")
LG.f2.6.0.5.25.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.25.ord.sd2,"safe")
LG.f2.6.0.5.26.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.26.ord.sd2,"safe")
LG.f2.6.0.5.27.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.27.ord.sd2,"safe")
LG.f2.6.0.5.28.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.28.ord.sd2,"safe")
LG.f2.6.0.5.29.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.29.ord.sd2,"safe")
LG.f2.6.0.5.30.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.30.ord.sd2,"safe")
LG.f2.6.0.5.31.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.31.ord.sd2,"safe")
LG.f2.6.0.5.32.ord.safe.sd2 <- make_seq(LG.f2.6.0.5.32.ord.sd2,"safe")

LG.f2.6.0.5.1.ord.all.sd2 <- make_seq(LG.f2.6.0.5.1.ord.sd2,"force")
LG.f2.6.0.5.2.ord.all.sd2 <- make_seq(LG.f2.6.0.5.2.ord.sd2,"force")
LG.f2.6.0.5.3.ord.all.sd2 <- make_seq(LG.f2.6.0.5.3.ord.sd2,"force")
LG.f2.6.0.5.4.ord.all.sd2 <- make_seq(LG.f2.6.0.5.4.ord.sd2,"force")
LG.f2.6.0.5.5.ord.all.sd2 <- make_seq(LG.f2.6.0.5.5.ord.sd2,"force")
LG.f2.6.0.5.6.ord.all.sd2 <- make_seq(LG.f2.6.0.5.6.ord.sd2,"force")
LG.f2.6.0.5.7.ord.all.sd2 <- make_seq(LG.f2.6.0.5.7.ord.sd2,"force")
LG.f2.6.0.5.8.ord.all.sd2 <- make_seq(LG.f2.6.0.5.8.ord.sd2,"force")
LG.f2.6.0.5.9.ord.all.sd2 <- make_seq(LG.f2.6.0.5.9.ord.sd2,"force")
LG.f2.6.0.5.10.ord.all.sd2 <- make_seq(LG.f2.6.0.5.10.ord.sd2,"force")
LG.f2.6.0.5.11.ord.all.sd2 <- make_seq(LG.f2.6.0.5.11.ord.sd2,"force")
LG.f2.6.0.5.12.ord.all.sd2 <- make_seq(LG.f2.6.0.5.12.ord.sd2,"force")
LG.f2.6.0.5.13.ord.all.sd2 <- make_seq(LG.f2.6.0.5.13.ord.sd2,"force")
LG.f2.6.0.5.14.ord.all.sd2 <- make_seq(LG.f2.6.0.5.14.ord.sd2,"force")
LG.f2.6.0.5.15.ord.all.sd2 <- make_seq(LG.f2.6.0.5.15.ord.sd2,"force")
LG.f2.6.0.5.16.ord.all.sd2 <- make_seq(LG.f2.6.0.5.16.ord.sd2,"force")
LG.f2.6.0.5.17.ord.all.sd2 <- make_seq(LG.f2.6.0.5.17.ord.sd2,"force")
LG.f2.6.0.5.18.ord.all.sd2 <- make_seq(LG.f2.6.0.5.18.ord.sd2,"force")
LG.f2.6.0.5.19.ord.all.sd2 <- make_seq(LG.f2.6.0.5.19.ord.sd2,"force")
LG.f2.6.0.5.20.ord.all.sd2 <- make_seq(LG.f2.6.0.5.20.ord.sd2,"force")
LG.f2.6.0.5.21.ord.all.sd2 <- make_seq(LG.f2.6.0.5.21.ord.sd2,"force")
LG.f2.6.0.5.22.ord.all.sd2 <- make_seq(LG.f2.6.0.5.22.ord.sd2,"force")
LG.f2.6.0.5.23.ord.all.sd2 <- make_seq(LG.f2.6.0.5.23.ord.sd2,"force")
LG.f2.6.0.5.24.ord.all.sd2 <- make_seq(LG.f2.6.0.5.24.ord.sd2,"force")
LG.f2.6.0.5.25.ord.all.sd2 <- make_seq(LG.f2.6.0.5.25.ord.sd2,"force")
LG.f2.6.0.5.26.ord.all.sd2 <- make_seq(LG.f2.6.0.5.26.ord.sd2,"force")
LG.f2.6.0.5.27.ord.all.sd2 <- make_seq(LG.f2.6.0.5.27.ord.sd2,"force")
LG.f2.6.0.5.28.ord.all.sd2 <- make_seq(LG.f2.6.0.5.28.ord.sd2,"force")
LG.f2.6.0.5.29.ord.all.sd2 <- make_seq(LG.f2.6.0.5.29.ord.sd2,"force")
LG.f2.6.0.5.30.ord.all.sd2 <- make_seq(LG.f2.6.0.5.30.ord.sd2,"force")
LG.f2.6.0.5.31.ord.all.sd2 <- make_seq(LG.f2.6.0.5.31.ord.sd2,"force")
LG.f2.6.0.5.32.ord.all.sd2 <- make_seq(LG.f2.6.0.5.32.ord.sd2,"force")

```

Drawing the genetic map

```{r}
Map.6.0.5.ord.safe.sd2 <- list(
LG.f2.6.0.5.1.ord.safe.sd2, 
LG.f2.6.0.5.2.ord.safe.sd2, 
LG.f2.6.0.5.3.ord.safe.sd2, 
LG.f2.6.0.5.4.ord.safe.sd2, 
LG.f2.6.0.5.5.ord.safe.sd2, 
LG.f2.6.0.5.6.ord.safe.sd2, 
LG.f2.6.0.5.7.ord.safe.sd2, 
LG.f2.6.0.5.8.ord.safe.sd2, 
LG.f2.6.0.5.9.ord.safe.sd2, 
LG.f2.6.0.5.10.ord.safe.sd2,
LG.f2.6.0.5.11.ord.safe.sd2,
LG.f2.6.0.5.12.ord.safe.sd2,
LG.f2.6.0.5.13.ord.safe.sd2,
LG.f2.6.0.5.14.ord.safe.sd2,
LG.f2.6.0.5.15.ord.safe.sd2,
LG.f2.6.0.5.16.ord.safe.sd2,
LG.f2.6.0.5.17.ord.safe.sd2,
LG.f2.6.0.5.18.ord.safe.sd2,
LG.f2.6.0.5.19.ord.safe.sd2,
LG.f2.6.0.5.20.ord.safe.sd2,
LG.f2.6.0.5.21.ord.safe.sd2,
LG.f2.6.0.5.22.ord.safe.sd2,
LG.f2.6.0.5.23.ord.safe.sd2,
LG.f2.6.0.5.24.ord.safe.sd2,
LG.f2.6.0.5.25.ord.safe.sd2,
LG.f2.6.0.5.26.ord.safe.sd2,
LG.f2.6.0.5.27.ord.safe.sd2,
LG.f2.6.0.5.28.ord.safe.sd2,
LG.f2.6.0.5.29.ord.safe.sd2,
LG.f2.6.0.5.30.ord.safe.sd2,
LG.f2.6.0.5.31.ord.safe.sd2,
LG.f2.6.0.5.32.ord.safe.sd2)

Map.6.0.5.ord.all.sd2 <- list(
LG.f2.6.0.5.1.ord.all.sd2, 
LG.f2.6.0.5.2.ord.all.sd2, 
LG.f2.6.0.5.3.ord.all.sd2, 
LG.f2.6.0.5.4.ord.all.sd2, 
LG.f2.6.0.5.5.ord.all.sd2, 
LG.f2.6.0.5.6.ord.all.sd2, 
LG.f2.6.0.5.7.ord.all.sd2, 
LG.f2.6.0.5.8.ord.all.sd2, 
LG.f2.6.0.5.9.ord.all.sd2, 
LG.f2.6.0.5.10.ord.all.sd2,
LG.f2.6.0.5.11.ord.all.sd2,
LG.f2.6.0.5.12.ord.all.sd2,
LG.f2.6.0.5.13.ord.all.sd2,
LG.f2.6.0.5.14.ord.all.sd2,
LG.f2.6.0.5.15.ord.all.sd2,
LG.f2.6.0.5.16.ord.all.sd2,
LG.f2.6.0.5.17.ord.all.sd2,
LG.f2.6.0.5.18.ord.all.sd2,
LG.f2.6.0.5.19.ord.all.sd2,
LG.f2.6.0.5.20.ord.all.sd2,
LG.f2.6.0.5.21.ord.all.sd2,
LG.f2.6.0.5.22.ord.all.sd2,
LG.f2.6.0.5.23.ord.all.sd2,
LG.f2.6.0.5.24.ord.all.sd2,
LG.f2.6.0.5.25.ord.all.sd2,
LG.f2.6.0.5.26.ord.all.sd2,
LG.f2.6.0.5.27.ord.all.sd2,
LG.f2.6.0.5.28.ord.all.sd2,
LG.f2.6.0.5.29.ord.all.sd2,
LG.f2.6.0.5.30.ord.all.sd2,
LG.f2.6.0.5.31.ord.all.sd2,
LG.f2.6.0.5.32.ord.all.sd2)

pdf("Map.6.0.5.ord.safe.sd2.pdf")
draw_map(Map.6.0.5.ord.safe.sd2, names= TRUE, grid=TRUE, cex.mrk=0.3)
dev.off()

pdf("Map.6.0.5.ord.all.sd2.pdf")
draw_map(Map.6.0.5.ord.all.sd2, names= TRUE, grid=TRUE, cex.mrk=0.3)
dev.off()

```

Linage group 2 has more of 50 cM between the majority of the markers and one remaining

```{r}

LG.f2.6.0.5.2.ord.safe2.sd2 <- LG.f2.6.0.5.2.ord.safe.sd2
LG.f2.6.0.5.2.ord.safe2.sd2$seq.rf <- LG.f2.6.0.5.2.ord.safe.sd2$seq.rf[-1]
LG.f2.6.0.5.2.ord.safe2.sd2$seq.phases <- LG.f2.6.0.5.2.ord.safe.sd2$seq.phases[-1]
LG.f2.6.0.5.2.ord.safe2.sd2$seq.num <- LG.f2.6.0.5.2.ord.safe.sd2$seq.num[-1]
LG.f2.6.0.5.2.ord.safe2.sd2

Map.6.0.5.ord.safe2.sd2 <- list(
LG.f2.6.0.5.1.ord.safe.sd2, 
LG.f2.6.0.5.2.ord.safe2.sd2, 
LG.f2.6.0.5.3.ord.safe.sd2, 
LG.f2.6.0.5.4.ord.safe.sd2, 
LG.f2.6.0.5.5.ord.safe.sd2, 
LG.f2.6.0.5.6.ord.safe.sd2, 
LG.f2.6.0.5.7.ord.safe.sd2, 
LG.f2.6.0.5.8.ord.safe.sd2, 
LG.f2.6.0.5.9.ord.safe.sd2, 
LG.f2.6.0.5.10.ord.safe.sd2,
LG.f2.6.0.5.11.ord.safe.sd2,
LG.f2.6.0.5.12.ord.safe.sd2,
LG.f2.6.0.5.13.ord.safe.sd2,
LG.f2.6.0.5.14.ord.safe.sd2,
LG.f2.6.0.5.15.ord.safe.sd2,
LG.f2.6.0.5.16.ord.safe.sd2,
LG.f2.6.0.5.17.ord.safe.sd2,
LG.f2.6.0.5.18.ord.safe.sd2,
LG.f2.6.0.5.19.ord.safe.sd2,
LG.f2.6.0.5.20.ord.safe.sd2,
LG.f2.6.0.5.21.ord.safe.sd2,
LG.f2.6.0.5.22.ord.safe.sd2,
LG.f2.6.0.5.23.ord.safe.sd2,
LG.f2.6.0.5.24.ord.safe.sd2,
LG.f2.6.0.5.25.ord.safe.sd2,
LG.f2.6.0.5.26.ord.safe.sd2,
LG.f2.6.0.5.27.ord.safe.sd2,
LG.f2.6.0.5.28.ord.safe.sd2,
LG.f2.6.0.5.29.ord.safe.sd2,
LG.f2.6.0.5.30.ord.safe.sd2,
LG.f2.6.0.5.31.ord.safe.sd2,
LG.f2.6.0.5.32.ord.safe.sd2)

pdf("Map.6.0.5.ord.safe2.sd2.pdf")
draw_map(Map.6.0.5.ord.safe2.sd2, names= TRUE, grid=TRUE, cex.mrk=0.3)
dev.off()
```

Linage group 2 has more of 50 cM between the majority of the markers and 13 at the end

```{r}

LG.f2.6.0.5.2.ord.safe3.sd2 <- LG.f2.6.0.5.2.ord.safe2.sd2
LG.f2.6.0.5.2.ord.safe3.sd2$seq.num <- LG.f2.6.0.5.2.ord.safe2.sd2$seq.num[1:23]
LG.f2.6.0.5.2.ord.safe3.sd2$seq.rf <- LG.f2.6.0.5.2.ord.safe2.sd2$seq.rf[1:22]
LG.f2.6.0.5.2.ord.safe3.sd2$seq.phases <- LG.f2.6.0.5.2.ord.safe2.sd2$seq.phases[1:22]
LG.f2.6.0.5.2.ord.safe3.sd2

Map.6.0.5.ord.safe3.sd2 <- list(
LG.f2.6.0.5.1.ord.safe.sd2, 
LG.f2.6.0.5.2.ord.safe3.sd2, 
LG.f2.6.0.5.3.ord.safe.sd2, 
LG.f2.6.0.5.4.ord.safe.sd2, 
LG.f2.6.0.5.5.ord.safe.sd2, 
LG.f2.6.0.5.6.ord.safe.sd2, 
LG.f2.6.0.5.7.ord.safe.sd2, 
LG.f2.6.0.5.8.ord.safe.sd2, 
LG.f2.6.0.5.9.ord.safe.sd2, 
LG.f2.6.0.5.10.ord.safe.sd2,
LG.f2.6.0.5.11.ord.safe.sd2,
LG.f2.6.0.5.12.ord.safe.sd2,
LG.f2.6.0.5.13.ord.safe.sd2,
LG.f2.6.0.5.14.ord.safe.sd2,
LG.f2.6.0.5.15.ord.safe.sd2,
LG.f2.6.0.5.16.ord.safe.sd2,
LG.f2.6.0.5.17.ord.safe.sd2,
LG.f2.6.0.5.18.ord.safe.sd2,
LG.f2.6.0.5.19.ord.safe.sd2,
LG.f2.6.0.5.20.ord.safe.sd2,
LG.f2.6.0.5.21.ord.safe.sd2,
LG.f2.6.0.5.22.ord.safe.sd2,
LG.f2.6.0.5.23.ord.safe.sd2,
LG.f2.6.0.5.24.ord.safe.sd2,
LG.f2.6.0.5.25.ord.safe.sd2,
LG.f2.6.0.5.26.ord.safe.sd2,
LG.f2.6.0.5.27.ord.safe.sd2,
LG.f2.6.0.5.28.ord.safe.sd2,
LG.f2.6.0.5.29.ord.safe.sd2,
LG.f2.6.0.5.30.ord.safe.sd2,
LG.f2.6.0.5.31.ord.safe.sd2,
LG.f2.6.0.5.32.ord.safe.sd2)

pdf("Map.6.0.5.ord.safe3.sd2.pdf")
draw_map(Map.6.0.5.ord.safe3.sd2, names= TRUE, grid=TRUE, cex.mrk=0.3)
dev.off()
```


Linage group 2 has more of 50 cM between the majority of the markers and 13 at the end

```{r}

LG.f2.6.0.5.17.ord.safe2.sd2 <- LG.f2.6.0.5.17.ord.safe.sd2
LG.f2.6.0.5.17.ord.safe2.sd2$seq.num <- LG.f2.6.0.5.17.ord.safe.sd2$seq.num[1:47]
LG.f2.6.0.5.17.ord.safe2.sd2$seq.rf <- LG.f2.6.0.5.17.ord.safe.sd2$seq.rf[1:46]
LG.f2.6.0.5.17.ord.safe2.sd2$seq.phases <- LG.f2.6.0.5.17.ord.safe.sd2$seq.phases[1:46]
LG.f2.6.0.5.17.ord.safe2.sd2

Map.6.0.5.ord.safe4.sd2 <- list(
LG.f2.6.0.5.1.ord.safe.sd2, 
LG.f2.6.0.5.2.ord.safe3.sd2, 
LG.f2.6.0.5.3.ord.safe.sd2, 
LG.f2.6.0.5.4.ord.safe.sd2, 
LG.f2.6.0.5.5.ord.safe.sd2, 
LG.f2.6.0.5.6.ord.safe.sd2, 
LG.f2.6.0.5.7.ord.safe.sd2, 
LG.f2.6.0.5.8.ord.safe.sd2, 
LG.f2.6.0.5.9.ord.safe.sd2, 
LG.f2.6.0.5.10.ord.safe.sd2,
LG.f2.6.0.5.11.ord.safe.sd2,
LG.f2.6.0.5.12.ord.safe.sd2,
LG.f2.6.0.5.13.ord.safe.sd2,
LG.f2.6.0.5.14.ord.safe.sd2,
LG.f2.6.0.5.15.ord.safe.sd2,
LG.f2.6.0.5.16.ord.safe.sd2,
LG.f2.6.0.5.17.ord.safe2.sd2,
LG.f2.6.0.5.18.ord.safe.sd2,
LG.f2.6.0.5.19.ord.safe.sd2,
LG.f2.6.0.5.20.ord.safe.sd2,
LG.f2.6.0.5.21.ord.safe.sd2,
LG.f2.6.0.5.22.ord.safe.sd2,
LG.f2.6.0.5.23.ord.safe.sd2,
LG.f2.6.0.5.24.ord.safe.sd2,
LG.f2.6.0.5.25.ord.safe.sd2,
LG.f2.6.0.5.26.ord.safe.sd2,
LG.f2.6.0.5.27.ord.safe.sd2,
LG.f2.6.0.5.28.ord.safe.sd2,
LG.f2.6.0.5.29.ord.safe.sd2,
LG.f2.6.0.5.30.ord.safe.sd2,
LG.f2.6.0.5.31.ord.safe.sd2,
LG.f2.6.0.5.32.ord.safe.sd2)

pdf("Map.6.0.5.ord.safe4.sd2.pdf")
draw_map(Map.6.0.5.ord.safe4.sd2, names= TRUE, grid=TRUE, cex.mrk=0.3)
dev.off()
```

Linage group 24 has more of 50 cM between the majority of the markers and the remaining 8

```{r}

LG.f2.6.0.5.24.ord.safe2.sd2 <- LG.f2.6.0.5.24.ord.safe.sd2
LG.f2.6.0.5.24.ord.safe2.sd2$seq.rf <- LG.f2.6.0.5.24.ord.safe.sd2$seq.rf[-c(1:8)]
LG.f2.6.0.5.24.ord.safe2.sd2$seq.phases <- LG.f2.6.0.5.24.ord.safe.sd2$seq.phases[-c(1:8)]
LG.f2.6.0.5.24.ord.safe2.sd2$seq.num <- LG.f2.6.0.5.24.ord.safe.sd2$seq.num[-c(1:8)]
LG.f2.6.0.5.24.ord.safe2.sd2

Map.6.0.5.ord.safe5.sd2 <- list(
LG.f2.6.0.5.1.ord.safe.sd2, 
LG.f2.6.0.5.2.ord.safe3.sd2, 
LG.f2.6.0.5.3.ord.safe.sd2, 
LG.f2.6.0.5.4.ord.safe.sd2, 
LG.f2.6.0.5.5.ord.safe.sd2, 
LG.f2.6.0.5.6.ord.safe.sd2, 
LG.f2.6.0.5.7.ord.safe.sd2, 
LG.f2.6.0.5.8.ord.safe.sd2, 
LG.f2.6.0.5.9.ord.safe.sd2, 
LG.f2.6.0.5.10.ord.safe.sd2,
LG.f2.6.0.5.11.ord.safe.sd2,
LG.f2.6.0.5.12.ord.safe.sd2,
LG.f2.6.0.5.13.ord.safe.sd2,
LG.f2.6.0.5.14.ord.safe.sd2,
LG.f2.6.0.5.15.ord.safe.sd2,
LG.f2.6.0.5.16.ord.safe.sd2,
LG.f2.6.0.5.17.ord.safe2.sd2,
LG.f2.6.0.5.18.ord.safe.sd2,
LG.f2.6.0.5.19.ord.safe.sd2,
LG.f2.6.0.5.20.ord.safe.sd2,
LG.f2.6.0.5.21.ord.safe.sd2,
LG.f2.6.0.5.22.ord.safe.sd2,
LG.f2.6.0.5.23.ord.safe.sd2,
LG.f2.6.0.5.24.ord.safe2.sd2,
LG.f2.6.0.5.25.ord.safe.sd2,
LG.f2.6.0.5.26.ord.safe.sd2,
LG.f2.6.0.5.27.ord.safe.sd2,
LG.f2.6.0.5.28.ord.safe.sd2,
LG.f2.6.0.5.29.ord.safe.sd2,
LG.f2.6.0.5.30.ord.safe.sd2,
LG.f2.6.0.5.31.ord.safe.sd2,
LG.f2.6.0.5.32.ord.safe.sd2)

pdf("Map.6.0.5.ord.safe5.sd2.pdf")
draw_map(Map.6.0.5.ord.safe5.sd2, names= TRUE, grid=TRUE, cex.mrk=0.3)
dev.off()
```

Finally, the linkage group 25 have over 40 cM between the majority of the markers and the last one


```{r}

LG.f2.6.0.5.25.ord.safe2 <- LG.f2.6.0.5.25.ord.safe
LG.f2.6.0.5.25.ord.safe2$seq.num <- LG.f2.6.0.5.25.ord.safe$seq.num[1:19]
LG.f2.6.0.5.25.ord.safe2$seq.rf <- LG.f2.6.0.5.25.ord.safe$seq.rf[1:18]
LG.f2.6.0.5.25.ord.safe2$seq.phases <- LG.f2.6.0.5.25.ord.safe$seq.phases[1:18]
LG.f2.6.0.5.25.ord.safe2

Map.6.0.5.ord.safe4 <- list(
LG.f2.6.0.5.1.ord.safe, 
LG.f2.6.0.5.2.ord.safe2, 
LG.f2.6.0.5.3.ord.safe, 
LG.f2.6.0.5.4.ord.safe, 
LG.f2.6.0.5.5.ord.safe, 
LG.f2.6.0.5.6.ord.safe, 
LG.f2.6.0.5.7.ord.safe, 
LG.f2.6.0.5.8.ord.safe, 
LG.f2.6.0.5.9.ord.safe, 
LG.f2.6.0.5.10.ord.safe,
LG.f2.6.0.5.11.ord.safe,
LG.f2.6.0.5.12.ord.safe,
LG.f2.6.0.5.13.ord.safe,
LG.f2.6.0.5.14.ord.safe,
LG.f2.6.0.5.15.ord.safe,
LG.f2.6.0.5.16.ord.safe,
LG.f2.6.0.5.17.ord.safe,
LG.f2.6.0.5.18.ord.safe,
LG.f2.6.0.5.19.ord.safe,
LG.f2.6.0.5.20.ord.safe,
LG.f2.6.0.5.21.ord.safe,
LG.f2.6.0.5.22.ord.safe,
LG.f2.6.0.5.23.ord.safe,
LG.f2.6.0.5.24.ord.safe2,
LG.f2.6.0.5.25.ord.safe2,
LG.f2.6.0.5.26.ord.safe,
LG.f2.6.0.5.27.ord.safe,
LG.f2.6.0.5.28.ord.safe,
LG.f2.6.0.5.29.ord.safe,
LG.f2.6.0.5.30.ord.safe,
LG.f2.6.0.5.31.ord.safe,
LG.f2.6.0.5.32.ord.safe)

draw.map(Map.6.0.5.ord.safe4, names= TRUE, grid=TRUE, cex.mrk=0.3)